---
title: "Customer Enquiries analysis"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(Enquiries)
library(readr)
library(dplyr)
library(plyr)
library(tidyr)
library(ggplot2)
library(stringr)
library(ABR)
library(lubridate)
library(sqldf)
library(randomNames)
library(data.table)

```

## GitHub Documents

This is an R Markdown format used for publishing markdown documents to GitHub. When you click the **Knit** button all R code chunks are run and a markdown file (.md) suitable for publishing to GitHub is generated.

read in the annual call qualifier data 

```{r load}
conn <- ABR::PostgreSQLconnect()

CallQual <- read_delim("N:/ABR/GENTRACK DATA/data AGAIN  for phil 22 nov.txt", 
                    delim = "|") 

```

fix any parsing failures due to inconsistent delimeters

```{r fix parsing fails}
Clean_df <- function(input) {
    probs_location <- input[problems(input)$row,]
    
    col <- unique(problems(input)$col[!is.na(problems(input)$col)])
    
    col <- vapply(col, function(x) which(x == colnames(input)), numeric(1))
    
    probs <- data.frame(problems(input)) %>% select(row, col) %>% distinct
    
    probs$idx <- ""
    probs$idx[!is.na(probs$col)] <- as.numeric(vapply(probs$col[!is.na(probs$col)], function(x) col[x], numeric(1))) 
    
    probs$idx <- as.numeric(probs$idx)
    
    probs$df <- ""
    
    probs$df[!is.na(probs$idx)] <- unname(vapply(which(!is.na(probs$idx)), function(i) grepl("\\r\\n", input[[probs$row[i], probs$idx[i]]]), logical(1)))
    
    df <- probs[probs$df == TRUE,]
    
    if(nrow(df) == 0) {
      return(NA)
    }
    
    #dfs <- lapply(1:nrow(df), function(i) Clean_df(read_delim(input[[df$row[i], df$idx[i]]], delim = "|", skip = 1, col_names = FALSE)))
    
    dfs <- lapply(1:nrow(df), function(i) c(dfs, input[[df$row[i], df$idx[i]]]))
    
    dfs2 <- lapply(1:nrow(df), function(i) c(dfs, Clean_df(read_delim(input[[df$row[i], df$idx[i]]], delim = "|", skip = 1, col_names = FALSE))))
    
    
return(unlist(dfs2))

}

dfs <- ""

clean <- Clean_df(CallQual)

clean2 <- unique(clean[!is.na(clean) & clean != ""])

correct2 <- lapply(clean2, function(x) read_delim(x, delim = "|", skip = 1, col_names = FALSE))

#correct3 <- correct2[lapply(correct2, !is.na)]

cor_time <- function(df) {

  x <- df[lapply(df, is.POSIXct) == TRUE] 
  df[lapply(df, is.POSIXct) == TRUE] <- lapply(x, function(x) dmy_hms(format(x, format="%y-%m-%d %H:%M:%S")))
  
  return(df)
}

correct3 <- ldply(correct2, cor_time) %>% distinct

colnames(correct3) <- colnames(CallQual)

CallQual2 <- cor_time(CallQual) %>% distinct

CallQual3 <- rbind(correct3, CallQual2) %>% distinct

rm(CallQual, CallQual2, correct2, correct3, clean, clean2)

dbWriteTable(con=conn,
             name="CallQual3",
             value=CallQual3,
             row.names=FALSE,
             append=TRUE)

CallQual3 <- dbReadTable(con=conn,
                         name="CallQual3")

```

Extract data form the MEC notes

```{r organise memo information}

library(purrr)

names <- randomNames(n = 2000000, which.names = "first")

Clean <- function(CallQual) { 
  
    CallQual$ENQUIRY <- ""
    
    p.1 <- "(.[^=]*)=(.[^-]*)"
    idx <- grepl(p.1, CallQual$MEMO_POS1)
    CallQual$ENQUIRY[idx] <- gsub(p.1, "\\2",  CallQual$MEMO_POS1[idx])
    
    p.2 <- "(.[^=]*):"
    idx <- grepl(p.2, CallQual$MEMO_POS1)
    #CallQual$ENQUIRY[idx] <- gsub(p.2, "\\2",  CallQual$MEMO_POS1[idx])
    CallQual$ENQUIRY[idx] <- paste(CallQual$MEMO_POS1[idx], CallQual$MEMO_POS2[idx]) 
    
    id <- logical(length(CallQual$ENQUIRY[idx]))
    
    id[grepl("bill", CallQual$ENQUIRY[idx])] <- "ACCOUNT INFORMATION"
    id[grepl("leak", CallQual$ENQUIRY[idx])] <- "METERING"
    id[grepl("update my details", CallQual$ENQUIRY[idx])] <- "ACCOUNT MAINTENANCE"
    id[grepl("payment arrangement", CallQual$ENQUIRY[idx])] <- "PAYMENTS"
    id[grepl("payment[^arrangement]", CallQual$ENQUIRY[idx])] <- "PAYMENTS"
    id[grepl("disconnection and reconnection", CallQual$ENQUIRY[idx])] <- "Water Serv Rbty"
    id[grepl("change the details", CallQual$ENQUIRY[idx])] <- "ACCOUNT MAINTENANCE"
    id[grepl("deceased", CallQual$ENQUIRY[idx])] <- "OWNER"
    id[grepl("final notice", CallQual$ENQUIRY[idx])] <- "ISSUE BILL"
    id[grepl("pension", CallQual$ENQUIRY[idx])] <- "CONCESSIONS & REBATES"
    id[grepl("no longer occupy", CallQual$ENQUIRY[idx])] <- "TENANCY"
    CallQual$ENQUIRY[idx][id == "FALSE"] <- "OTHER"
    
    CallQual$ENQUIRY[idx] <- id
    
    p.3 <- "(.*)-(.*)"
    idx <- grepl(p.3, CallQual$ENQUIRY)
    CallQual$ENQUIRY[idx] <- gsub(p.3, "\\1", CallQual$ENQUIRY[idx])
    
    enquiry <- unique(CallQual$ENQUIRY)
    
    idx <- lapply(enquiry, function(x) which(grepl(x, enquiry[-which(enquiry == x)]) == TRUE) + 1)
    
    names(idx) <- enquiry
    
    idx <- idx[lapply(idx, length) > 0]
    
    idx <- lapply(idx, function(x) which(grepl(paste(enquiry[x], collapse = "|"), CallQual$ENQUIRY)))
    
    lapply(names(idx), function(i) CallQual$ENQUIRY[idx[[i]]] <<- i)
    
    split <- strsplit(enquiry, "\\W+")
    
    # idx <- lapply(split, function(x) any(tolower(x) == tolower(names)))
    
    # wordcount <- vapply(split, length, integer(1))
    # 
    # keys <- enquiry[wordcount <= 5]
    # 
    # CallQual$ENQUIRY <- str_trim(CallQual$ENQUIRY)
    # 
    # lapply(seq_along(idx), function(i) keys[unlist(idx[i])] <- keys[i])
    # 
    # keys <- keys[!tolower(keys) %in% tolower(names)]
    # 
    # id <- !(CallQual$RESULT %in% keys)
    # 
    # CallQual$MEMO_POS2[id] <- str_trim(paste(CallQual$MEMO_POS2[id], CallQual$RESULT[id], sep = " "))
    
    # CallQual$RESULT[id] <- ""
    
    
    CallQual$ACTION <- ""
    
    fix <- "(-|not|payment)$"
    idx <- grepl(fix, CallQual$MEMO_POS2)
    
    CallQual$MEMO_POS2[idx] <- paste(CallQual$MEMO_POS2[idx], CallQual$MEMO_POS3[idx])
    
    CallQual$MEMO_POS3[idx] <- ""
    
    fix <- "re-send"
    idx <- grepl(fix, CallQual$MEMO_POS2, ignore.case = TRUE)
    
    CallQual$MEMO_POS2[idx] <- gsub("re-send", "resend", CallQual$MEMO_POS2[idx], ignore.case = TRUE)
    
    p.1 <- "(.[^=]*)=(.[^-]*)-(.[^-]*)-(.[^-]*)"
    idx.1 <- grepl(p.1, CallQual$MEMO_POS2)  
    
    CallQual$ACTION[idx.1] <- gsub(p.1, "\\2 \\3", CallQual$MEMO_POS2[idx.1]) 
    
    p.2 <- "(.[^=]*)=(.[^-]*)-(.[^-]*)"
    idx.2 <- grepl(p.2, CallQual$MEMO_POS2)  
    
    CallQual$ACTION[idx.2 & !idx.1] <- gsub(p.2, "\\2", CallQual$MEMO_POS2[idx.2 & !idx.1]) 
    
    p.3 <- "(.[^=]*)=(.[^-]*)"
    idx.3 <- grepl(p.3, CallQual$MEMO_POS2)  
    
    CallQual$ACTION[idx.3 & !idx.2 & !idx.1] <- gsub(p.3, "\\2", CallQual$MEMO_POS2[idx.3 & !idx.2 & !idx.1]) 
    
    CallQual$RESULT <- ""
    
    p.1 <- "(.[^=]*)=(.[^-]*)-(.[^-]*)-(.[^-]*)"
    idx.1 <- grepl(p.1, CallQual$MEMO_POS2)  
    
    CallQual$RESULT[idx.1] <- gsub(p.1, "\\4", CallQual$MEMO_POS2[idx.1]) 
    
    p.2 <- "(.[^=]*)=(.[^-]*)-(.[^-]*)"
    idx.2 <- grepl(p.2, CallQual$MEMO_POS2)  
    
    CallQual$RESULT[idx.2 & !idx.1] <- gsub(p.2, "\\3", CallQual$MEMO_POS2[idx.2 & !idx.1]) 
    
    p.3 <- "(.[^=]*)=(.[^-]*)"
    idx.3 <- grepl(p.3, CallQual$MEMO_POS2)  
    
    CallQual$RESULT[idx.3 & !idx.2 & !idx.1] <- ""
    
    CallQual$RESULT <- str_trim(CallQual$RESULT)
    
    #Clean the result column
    result <- unique(CallQual$RESULT)
    finalised <- paste(result[grepl("^f[^o].*", result, ignore.case = TRUE)], collapse = "|")
    id <- grepl(finalised, CallQual$RESULT, ignore.case = TRUE) 
    CallQual$RESULT[id] <- gsub(finalised, "Finalised", CallQual$RESULT[id], ignore.case = TRUE)
    
    result <- unique(CallQual$RESULT)
    referred <- paste(result[grepl("^ref.*[^L]$", result, ignore.case = TRUE)], collapse = "|")
    id <- grepl(referred, CallQual$RESULT, ignore.case = TRUE) 
    CallQual$RESULT[id] <- gsub(referred, "Referred", CallQual$RESULT[id], ignore.case = TRUE)
    
    result <- unique(CallQual$RESULT)
    crel <- paste(result[grepl("^ref.*[L]$", result, ignore.case = TRUE)], collapse = "|")
    id <- grepl(crel, CallQual$RESULT, ignore.case = TRUE) 
    CallQual$RESULT[id] <- gsub(crel, "ReferredCREL", CallQual$RESULT[id], ignore.case = TRUE)
    
    result <- unique(CallQual$RESULT)
    
    split <- strsplit(result, "\\W+")
    
    wordcount <- vapply(split, length, integer(1))
    
    keys <- result[wordcount <= 2]
    
    keys <- keys[!tolower(keys) %in% tolower(names)]
    
    id <- !(CallQual$RESULT %in% keys)
    
    CallQual$MEMO_POS2[id] <- str_trim(paste(CallQual$MEMO_POS2[id], CallQual$RESULT[id], sep = " "))
    
    CallQual$RESULT[id] <- ""
    
    CallQual[,17:24][is.na(CallQual[,17:24])] <- ""
    
    idx <- grepl("[0-9]+/[0-9]+/[0-9]+", CallQual$USES)
    
    idx.2 <- !is.na(CallQual$MEMO_POS10)
    
    CallQual[idx & idx.2,]$MEMO_POS9 <- paste(CallQual[idx & idx.2,]$MEMO_POS9, CallQual[idx & idx.2,]$MEMO_POS10)
    
    CallQual[idx,25:33] <- CallQual[idx,26:34]
    
    CallQual <- CallQual %>%
                 mutate(MEMO = paste(MEMO_POS3, 
                                    MEMO_POS4,
                                    MEMO_POS5,
                                    MEMO_POS6,
                                    MEMO_POS7,
                                    MEMO_POS8,
                                    MEMO_POS9,
                                    MEMO_POS10,
                                    sep = " "))
    
    
    
    
return(CallQual)
}

CallQual4 <- Clean(CallQual3) #to do: need to fix ENQUIRY = FALSE#

rm(CallQual3)

dbWriteTable(con=conn,
             name="CallQual4",
             value=CallQual4,
             row.names=FALSE,
             append=TRUE)

CallQual4 <- dbReadTable(con=conn,
                         name="CallQual4")

CallQual5 <- CallQual4[!grepl("^RES|NONRES", CallQual4$USES),] 

row.names(CallQual5) <- CallQual5$MEMO_ID

x <- apply(CallQual5, 1, function(x) which(grepl("^RES|^NONRES", x) == TRUE))

x[lapply(x, )]

x[lapply(x,length) == 0] <- 27

x <- unlist(unname(x))

y <- lapply(1:nrow(CallQual5), function(i) CallQual5[[i,x[i]]]) 

dbWriteTable(con=conn,
             name="CallQual5",
             value=CallQual5,
             row.names=FALSE,
             append=TRUE)

cols <- vapply(CallQual4, is.character, logical(1))

CallQual4[ , cols] <- apply(CallQual4[ , cols], 2, str_trim)
CallQual4[ , cols] <- apply(CallQual4[ , cols], 2, toupper)

dbWriteTable(con=conn,
             name="Callqual_281116",
             value=CallQual4,
             row.names=FALSE,
             append=TRUE)


#CallQual2$ENQUIRY = sapply(CallQual2$MEMO_POS1, Enquiry)
result = lapply(CallQual2$MEMO_POS2, Result)
names(result) <- CallQual2$MEMO_CONSUMER
result_tbl <- ldply(result)


```

Create a call ID

```{r Call ID}

#CallQual2 <- CallQual3

#CallQual3 <- data.table(CallQual2)

#CallID1 <- CallQual3[, MEMO_DATETIME := ymd_hms(MEMO_DATETIME)][, time_window := MEMO_DATETIME + minutes(5)][,.(MEMO_CONSUMER, MEMO_ID, #MEMO_DATETIME, time_window)]

#setkey(CallID1, MEMO_DATETIME, time_window)

#CallID2 <- CallQual3[, MEMO_DATETIME := ymd_hms(MEMO_DATETIME)][, dummy := MEMO_DATETIME][,.(MEMO_CONSUMER, MEMO_ID, MEMO_DATETIME, dummy)]

#CallID3 <- sqldf("SELECT DISTINCT 
                  #a.MEMO_CONSUMER,
                  #a.MEMO_ID,
                  #a.MEMO_ID AS id,
                  #b.MEMO_ID AS parent
                  #FROM CallQual3 a
                  #LEFT JOIN CallQual3 b ON datetime(b.MEMO_DATETIME) >= (datetime(a.MEMO_DATETIME) - 'interval 5 mins') 
                  #AND datetime(b.MEMO_DATETIME) <= datetime(a.MEMO_DATETIME) 
                  #AND b.MEMO_CONSUMER = a.MEMO_CONSUMER 
                  #AND b.MEMO_ID <> a.MEMO_ID",
                  #drv = 'SQLite')

#Memo_call <- foverlaps(CallID2, 
                       #CallID1, 
                       #by.x=c("MEMO_DATETIME", "dummy"), 
                       #type = "within", 
                       #mult = "all")

Memo_calls <- dbReadTable(con=conn,
                         name="memo_calls")

x <- Memo_calls[Memo_calls$MEMO_CONSUMER == 22513504514,][,3:4]
x <- Memo_calls[Memo_calls$MEMO_CONSUMER == 22513554612,][,3:4]

path <- function(x) {
  #data.frame(id = x[,1], parent = x[,dim(x)[2]])
  df <- x
  while(any(!is.na(df[,dim(df)[2]]))) {
    
    df <- left_join(x, df, by = c("id" = "parent"))
    #df <- left_join(x, x[,c(dim(x)[2] -1,dim(x)[2])], by = c("id" = "parent"))
    
    #df2 <- df[,c(dim(df)[2], 1)] 
    
    #colnames(df2)[1] <- "id"
    
    #x <- union_all(df, df2)
  
  }
  
  df2 <- gather(df, join, child, 4:ncol(df)) %>% filter(is.na(parent))
  df3 <- df2 %>% filter(!is.na(child)) %>% select(child,id)
  colnames(df3) <- c("id", "parent")
  
  result <- rbind(df2 %>% select(id, parent), df3) %>% distinct()
 
  return(result)
}

library(nlme)
x <- Memo_calls[,c(1,3:4)]

y <- x %>% sample_n(100) %>% mutate(ID = MEMO_CONSUMER) %>% select(ID, id, parent) %>% group_by(ID)

z <- gapply(y, path)

result <- path(x)


gps <- data.frame(lapply(parents, is.na))

parents <- parents[unlist(lapply(1:nrow(gps), function(i) all(gps[i,3:ncol(gps)] == TRUE))) == FALSE,]

gps <- data.frame(lapply(parents, is.na))

parents[!gps] <- NULL


apply(gps,1,function(x) all())

path <- function(x) {
  
  #if(all(is.na(x[,dim(x)[2]]))) {
  
    #x[,dim(x)[2] + 1] <- left_join(x, x, by = c("id" = "parent"))
    
  #}
  
  if(any(!is.na(x[,dim(x)[2]]))) {  
  
    x[,dim(x)[2] + 1] <- left_join(x, path(x), by = c("id" = "parent"))$id.y
    #df <- %>% distinct
    }

}

#Memo_call<- Memo_call[MEMO_ID == i.MEMO_ID, i.MEMO_ID := 0][MEMO_ID != i.MEMO_ID & MEMO_CONSUMER == i.MEMO_CONSUMER][,.(MEMO_CONSUMER, #MEMO_ID,i.MEMO_ID)][, parent := MEMO_ID]

#names(Memo_call) <- c("MEMO_CONSUMER","MEMO_ID","parent","id" )

#Memo_call2 <- Memo_call[order(-rank(MEMO_CONSUMER), MEMO_ID)]

#Memo_call3 <- Memo_call2[]

```



```{r Key Accounts}
PropertyLayer <- read.csv("file:///N:/KarlBlackhall/Gentrack AL/PROPERTY_LAYER_1516FY (Q1-Q4).csv",
                          stringsAsFactors = FALSE) %>%
                 mutate(ACC_NAME = gsub("[[:space:]]|[^[:alnum:]]", "", ACCOUNT_NAME))

KeyAccounts <- read.csv("file:///C:/Enquiries/data/KeyAccounts.csv",
                        stringsAsFactors = FALSE) %>%
               mutate(ACCOUNT_NAME = str_trim(gsub("(.+)(\\(.+)", "\\1", Key.Customer))) %>%
               select(ACCOUNT_NAME) 


KeyAccountsName <- unique(gsub("[[:space:]]|[^[:alnum:]]", "", KeyAccounts$ACCOUNT_NAME))

link <- lapply(KeyAccountsName, function(x) PropertyLayer$MASTERID[which(grepl(x, PropertyLayer$ACC_NAME, ignore.case = TRUE) == TRUE)])

KeyAccountsID <- data.frame(MASTERID = unlist(link)) %>%
                 left_join(select(PropertyLayer, MASTERID, ACCOUNT_NAME)) %>%
                 distinct()

write.csv(KeyAccountsID, "data/KeyAccountsID.csv")

```

```{r Trade Waste}


```

```{r Annual plot}

EnquiryCountAnnual <- ddply(CallQual4, .(ENQUIRY, USES), summarise, Total = length(MEMO_CONSUMER)) %>%
                      arrange(-Total) %>%
                      select(USES,
                             ENQUIRY,
                             Total)

p1Annual <- ggplot(data = EnquiryCountAnnual,
             aes(x = factor(USES),
                 fill= factor(ENQUIRY),
                 y = Total)) 

p1Annual <- p1Annual + geom_bar(stat="identity")

#p1Annual <- p1Annual + facet_grid(facets=USES~SRM)

```

```{r Random code}

CallQual3 <- CallQual %>% 
             select(-MEMO_POS1:-MEMO_POS10) %>% 
             cbind(MemoNotes) %>% 
             mutate(SRM = ifelse(!is.na(SR_SERV_CODE), TRUE, FALSE),
                    MEMO_DATETIME = ymd_hms(format(MEMO_DATETIME, format="%d-%m-%y %H:%M:%S")),
                    SR_DATETIME = ymd_hms(format(SR_DATETIME, format="%d-%m-%y %H:%M:%S")),
                    CUS_BIRTHDATE = dmy(format(CUS_BIRTHDATE, format="%d/%m/%y")),
                    STAT_DATE = dmy(format(STAT_DATE, format="%d/%m/%y"))) %>%
             arrange(MEMO_CONSUMER, MEMO_DATETIME) #%>%
             #mutate(TIME_DIFF = difftime(MEMO_DATETIME, lag(MEMO_DATETIME, 1), units = "mins"),
                    #CALL_ID = seq(1, length(MEMO_CONSUMER), by = 1),
                    #CONSUMER_LAG = lag(MEMO_CONSUMER, 1)) %>%
                    #mutate(CALL_ID = ifelse(TIME_DIFF >= 0 & TIME_DIFF <= 5 & CONSUMER_LAG == MEMO_CONSUMER, lag(CALL_ID, 1), CALL_ID)) %>%
                    #mutate(CALL_ID2 = ifelse(CALL_ID == lag(CALL_ID, 1), CALL_ID, lag(CALL_ID, 1) + 1))

#CallQual4 <- CallQual3[-problems(CallQual)$row,]

#CWW_DW <- odbcDriverConnect(connection="Driver={SQL Server Native Client 11.0};
                            #server=wvdb1devsql;
                            #database=CWW_DW;
                            #uid=report;
                            #pwd=report")

#sqlSave(CWW_DW, CallQual, tablename='ABR_callqual_1516', rownames=F)

dbWriteTable(con=conn,
             name="dbo.abr_callqual_1516",
             value=CallQual2,
             row.names=FALSE,
             append=TRUE)

lines <- readLines("C:/Enquiries/SQL/Create_tables.sql", skipNul = TRUE)

sql_command =  paste(lines, collapse=" ")

dbGetQuery(sql_command, con = conn)

lines <- readLines("C:/Enquiries/SQL/Memo_id.sql", skipNul = TRUE)

sql_command =  paste(lines, collapse=" ")

dbGetQuery(sql_command, con = conn)

Unique_MEC <- unique(CallQual4$MEC)
Unique_MEC1 <- unique(CallQual4$MEC.1)

CallQual4 <- CallQual3 %>%
             select(MEMO_CONSUMER, 
                    MEMO_DATETIME,
                    TIME_DIFF,
                    CALL_ID,
                    CONSUMER_LAG)

```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
