---
title: "Non-residential SRM analysis 2014-2016"
author: "Phil Farrell"
date: "22 December 2016"
runtime: shiny
output: html_document
---

```{r, include=FALSE}

eval_cell = FALSE

```

####Setup

```{r setup script, message=FALSE, warning=FALSE, include=FALSE}

#setwd("C:/Enquiries")
knitr::opts_chunk$set(echo = TRUE)

packages <- c("readr", "dplyr", "plyr", "tidyr", "ggplot2", "stringr", "lubridate", "sqldf", "randomNames", "data.table", "devtools", "scales", "knitr", "xtable", "stringi", "shiny")

p <- installed.packages()

#install.packages(pkgs = packages[!(packages %in% row.names(p))])

library(devtools)

ifelse(!("rCharts" %in% row.names(p)), install_github('ramnathv/rCharts'), TRUE)

library(Enquiries)
#library(ABR)
library(rCharts)

lapply(packages, require, character.only = TRUE)

```

```{r load, eval= eval_cell, message=FALSE, warning=FALSE, include=FALSE}

CallQual <- read_delim("N:/ABR/GENTRACK DATA/data AGAIN  for phil 22 nov.txt", 
                    delim = "|", quote = "") #quote = "" is important to avoid parsing failures

```

```{r organise memo information, eval= eval_cell, message=FALSE, warning=FALSE, include=FALSE}

filter <- !(as.numeric(row.names(CallQual)) %in% problems(CallQual)$row)

CallQual2 <- CallQual[filter,]

names <- unique(randomNames(n = 2000000, which.names = "first"))

Clean <- function(CallQual) { 
    
    ##Create the Enquiry column
  
    CallQual$ENQUIRY <- ""
    
    p.1 <- "(.[^=]*)=(.[^-]*)"
    idx <- grepl(p.1, CallQual$MEMO_POS1)
    CallQual$ENQUIRY[idx] <- gsub(p.1, "\\2",  CallQual$MEMO_POS1[idx])
    
    p.2 <- "(.[^=]*):"
    idx <- grepl(p.2, CallQual$MEMO_POS1)
    #CallQual$ENQUIRY[idx] <- gsub(p.2, "\\2",  CallQual$MEMO_POS1[idx])
    CallQual$ENQUIRY[idx] <- paste(CallQual$MEMO_POS1[idx], CallQual$MEMO_POS2[idx]) 
    
    id <- logical(length(CallQual$ENQUIRY[idx]))
    
    id[grepl("bill", CallQual$ENQUIRY[idx])] <- "ACCOUNT INFORMATION"
    id[grepl("leak", CallQual$ENQUIRY[idx])] <- "METERING"
    id[grepl("update my details", CallQual$ENQUIRY[idx])] <- "ACCOUNT MAINTENANCE"
    id[grepl("payment arrangement", CallQual$ENQUIRY[idx])] <- "PAYMENTS"
    id[grepl("payment[^arrangement]", CallQual$ENQUIRY[idx])] <- "PAYMENTS"
    id[grepl("disconnection and reconnection", CallQual$ENQUIRY[idx])] <- "Water Serv Rbty"
    id[grepl("change the details", CallQual$ENQUIRY[idx])] <- "ACCOUNT MAINTENANCE"
    id[grepl("deceased", CallQual$ENQUIRY[idx])] <- "OWNER"
    id[grepl("final notice", CallQual$ENQUIRY[idx])] <- "ISSUE BILL"
    id[grepl("pension", CallQual$ENQUIRY[idx])] <- "CONCESSIONS & REBATES"
    id[grepl("no longer occupy", CallQual$ENQUIRY[idx])] <- "TENANCY"
    CallQual$ENQUIRY[idx][id == "FALSE"] <- "OTHER"
    
    CallQual$ENQUIRY[idx] <- id
    
    p.3 <- "(.*)-(.*)"
    idx <- grepl(p.3, CallQual$ENQUIRY)
    CallQual$ENQUIRY[idx] <- gsub(p.3, "\\1", CallQual$ENQUIRY[idx])
    
    enquiry <- unique(CallQual$ENQUIRY)
    
    idx <- lapply(enquiry, function(x) which(grepl(x, enquiry[-which(enquiry == x)]) == TRUE) + 1)
    
    names(idx) <- enquiry
    
    idx <- idx[lapply(idx, length) > 0]
    
    idx <- lapply(idx, function(x) which(grepl(paste(enquiry[x], collapse = "|"), CallQual$ENQUIRY)))
    
    lapply(names(idx), function(i) CallQual$ENQUIRY[idx[[i]]] <<- i)
    
    split <- strsplit(enquiry, "\\W+")
    
    if(length(CallQual[CallQual$ENQUIRY == "CUSTOMER CORRESPONDENCDE",]$ENQUIRY != 0)) {
    
      CallQual[CallQual$ENQUIRY == "CUSTOMER CORRESPONDENCDE",]$ENQUIRY <- "CUSTOMER CORRESPONDENCE"
      
    }
    
    # idx <- lapply(split, function(x) any(tolower(x) == tolower(names)))
    
    # wordcount <- vapply(split, length, integer(1))
    # 
    # keys <- enquiry[wordcount <= 5]
    # 
    # CallQual$ENQUIRY <- str_trim(CallQual$ENQUIRY)
    # 
    # lapply(seq_along(idx), function(i) keys[unlist(idx[i])] <- keys[i])
    # 
    # keys <- keys[!tolower(keys) %in% tolower(names)]
    # 
    # id <- !(CallQual$RESULT %in% keys)
    # 
    # CallQual$MEMO_POS2[id] <- str_trim(paste(CallQual$MEMO_POS2[id], CallQual$RESULT[id], sep = " "))
    
    # CallQual$RESULT[id] <- ""
    
    ## Create the action column
    CallQual$ACTION <- ""
    
    fix <- "(-|not|payment)$"
    idx <- grepl(fix, CallQual$MEMO_POS2)
    
    CallQual$MEMO_POS2[idx] <- paste(CallQual$MEMO_POS2[idx], CallQual$MEMO_POS3[idx])
    
    CallQual$MEMO_POS3[idx] <- ""
    
    fix <- "re-send"
    idx <- grepl(fix, CallQual$MEMO_POS2, ignore.case = TRUE)
    
    CallQual$MEMO_POS2[idx] <- gsub("re-send", "resend", CallQual$MEMO_POS2[idx], ignore.case = TRUE)
    
    p.1 <- "(.[^=]*)=(.[^-]*)-(.[^-]*)-(.[^-]*)"
    idx.1 <- grepl(p.1, CallQual$MEMO_POS2)  
    
    CallQual$ACTION[idx.1] <- gsub(p.1, "\\2 \\3", CallQual$MEMO_POS2[idx.1]) 
    
    p.2 <- "(.[^=]*)=(.[^-]*)-(.[^-]*)"
    idx.2 <- grepl(p.2, CallQual$MEMO_POS2)  
    
    CallQual$ACTION[idx.2 & !idx.1] <- gsub(p.2, "\\2", CallQual$MEMO_POS2[idx.2 & !idx.1]) 
    
    p.3 <- "(.[^=]*)=(.[^-]*)"
    idx.3 <- grepl(p.3, CallQual$MEMO_POS2)  
    
    CallQual$ACTION[idx.3 & !idx.2 & !idx.1] <- gsub(p.3, "\\2", CallQual$MEMO_POS2[idx.3 & !idx.2 & !idx.1]) 
    
    #Clean the action column
    
    CallQual$ACTION <- str_trim(CallQual$ACTION)
    
    action <- unique(CallQual$ACTION)
    
    split <- strsplit(action, "\\W+")
    
    wordcount <- vapply(split, length, integer(1))
    
    action <- action[wordcount >= 3]
    
    idx <- lapply(action, function(x) which(grepl(x, action) == TRUE))
    
    names(idx) <- action
    
    idx <- idx[lapply(idx, length) > 1]
    
    idx <- lapply(idx, function(x) action[x])
    
    lapply(names(idx), function(i) CallQual$ACTION[CallQual$ACTION %in% idx[[i]]] <<- i)
    
    idx <- lapply(idx, function(x) which(grepl(paste(action[x], collapse = "|"), CallQual$ACTION)))
    
    lapply(names(idx), function(i) CallQual$ACTION[idx[[i]]] <<- i)
    
    action <- unique(CallQual$ACTION)
    
    split <- strsplit(tolower(action), "\\W+")
    
    wordcount <- vapply(split, length, integer(1))
    
    keys <- action[wordcount >= 7]
    
    filter <- split[wordcount >= 7]
    
    idx <- keys[unlist(lapply(filter, function(x) any((x %in% tolower(names) == TRUE))))]
    
    idx2 <- lapply(action, function(x) which(grepl(x, idx[x != idx]) == TRUE))
    
    names(idx2) <- action
    
    idx2 <- idx2[lapply(idx2, length) > 0 & names(idx2) != ""]
    
    idx3 <- ldply(idx2, function(x) idx[x]) %>%
            group_by(V1) %>%
            filter(.id == .id[which.max(nchar(.id))]) %>%
            ungroup()
    
    lapply(1:nrow(idx3), function(i) CallQual$ACTION[CallQual$ACTION == idx3$V1[i]] <<- idx3$.id[i])
    
    unknown <- idx[!(idx %in% idx3$V1)]
    
    lapply(seq_along(unknown), function(i) CallQual$ACTION[CallQual$ACTION == unknown[i]] <<- "")
    
    # action <- unique(CallQual$ACTION)
    # 
    # split <- strsplit(tolower(action), "\\W+")
    # 
    # wordcount <- vapply(split, length, integer(1))
    # 
    # keys <- action[wordcount >= 8]
    # 
    # id <- !(CallQual$RESULT %in% keys)
    # 
    # CallQual$MEMO_POS2[id] <- str_trim(paste(CallQual$MEMO_POS2[id], CallQual$RESULT[id], sep = " "))
    # 
    # CallQual$RESULT[id] <- ""
    
    ##Create the result column
    CallQual$RESULT <- ""
    
    p.1 <- "(.[^=]*)=(.[^-]*)-(.[^-]*)-(.[^-]*)"
    idx.1 <- grepl(p.1, CallQual$MEMO_POS2)  
    
    CallQual$RESULT[idx.1] <- gsub(p.1, "\\4", CallQual$MEMO_POS2[idx.1]) 
    
    p.2 <- "(.[^=]*)=(.[^-]*)-(.[^-]*)"
    idx.2 <- grepl(p.2, CallQual$MEMO_POS2)  
    
    CallQual$RESULT[idx.2 & !idx.1] <- gsub(p.2, "\\3", CallQual$MEMO_POS2[idx.2 & !idx.1]) 
    
    p.3 <- "(.[^=]*)=(.[^-]*)"
    idx.3 <- grepl(p.3, CallQual$MEMO_POS2)  
    
    CallQual$RESULT[idx.3 & !idx.2 & !idx.1] <- ""
    
    CallQual$RESULT <- str_trim(CallQual$RESULT)
    
    #Clean the result column
    result <- unique(CallQual$RESULT)
    finalised <- paste(result[grepl("^f[^o].*", result, ignore.case = TRUE)], collapse = "|")
    id <- grepl(finalised, CallQual$RESULT, ignore.case = TRUE) 
    CallQual$RESULT[id] <- gsub(finalised, "Finalised", CallQual$RESULT[id], ignore.case = TRUE)
    
    result <- unique(CallQual$RESULT)
    referred <- paste(result[grepl("^ref.*[^L]$", result, ignore.case = TRUE)], collapse = "|")
    id <- grepl(referred, CallQual$RESULT, ignore.case = TRUE) 
    CallQual$RESULT[id] <- gsub(referred, "Referred", CallQual$RESULT[id], ignore.case = TRUE)
    
    result <- unique(CallQual$RESULT)
    crel <- paste(result[grepl("^ref.*[L]$", result, ignore.case = TRUE)], collapse = "|")
    id <- grepl(crel, CallQual$RESULT, ignore.case = TRUE) 
    CallQual$RESULT[id] <- gsub(crel, "ReferredCREL", CallQual$RESULT[id], ignore.case = TRUE)
    
    result <- unique(CallQual$RESULT)
    
    split <- strsplit(result, "\\W+")
    
    wordcount <- vapply(split, length, integer(1))
    
    keys <- result[wordcount <= 2]
    
    keys <- keys[!tolower(keys) %in% tolower(names)]
    
    id <- !(CallQual$RESULT %in% keys)
    
    CallQual$MEMO_POS2[id] <- str_trim(paste(CallQual$MEMO_POS2[id], CallQual$RESULT[id], sep = " "))
    
    CallQual$RESULT[id] <- ""
    
    CallQual[,17:24][is.na(CallQual[,17:24])] <- ""
    
    idx <- grepl("[0-9]+/[0-9]+/[0-9]+", CallQual$USES)
    
    idx.2 <- !is.na(CallQual$MEMO_POS10)
    
    CallQual[idx & idx.2,]$MEMO_POS9 <- paste(CallQual[idx & idx.2,]$MEMO_POS9, CallQual[idx & idx.2,]$MEMO_POS10)
    
    CallQual[idx,25:33] <- CallQual[idx,26:34]
    
    idx <- !grepl("^RES|^NONRES", CallQual$USES)
    
    idx.2 <- !is.na(CallQual$MEMO_POS10)
    
    CallQual[idx & idx.2,]$MEMO_POS9 <- paste(CallQual[idx & idx.2,]$MEMO_POS9, CallQual[idx & idx.2,]$MEMO_POS10)
    
    CallQual[idx,25:33] <- CallQual[idx,26:34]
    
    CallQual <- CallQual %>%
                 mutate(MEMO = paste(MEMO_POS3, 
                                    MEMO_POS4,
                                    MEMO_POS5,
                                    MEMO_POS6,
                                    MEMO_POS7,
                                    MEMO_POS8,
                                    MEMO_POS9,
                                    MEMO_POS10,
                                    sep = " "))
    
    
    
    
return(CallQual)
}

CallQual3 <- Clean(CallQual2) #to do: need to fix ENQUIRY = FALSE#

rm(CallQual2)

cols <- vapply(CallQual3, is.character, logical(1))

CallQual3[ , cols] <- apply(CallQual3[ , cols], 2, str_trim)
CallQual3[ , cols] <- apply(CallQual3[ , cols], 2, toupper)

```

```{r Date time, message=FALSE, eval= eval_cell, warning=FALSE, include=FALSE}

CallQual3 <- CallQual3 %>%
                    mutate(SRM = ifelse(!is.na(SR_SERV_CODE), TRUE, FALSE),
                    MEMO_DATETIME = parse_date_time(MEMO_DATETIME, orders="%d-%m-%y %H:%M:%S"),
                    SR_DATETIME = parse_date_time(SR_DATETIME, orders="%d-%m-%y %H:%M:%S"),
                    CUS_BIRTHDATE = dmy(format(CUS_BIRTHDATE, format="%d/%m/%y")),
                    STAT_DATE = dmy(format(STAT_DATE, format="%d/%m/%y")))

```

```{r Key Accounts, eval= eval_cell, message=FALSE, warning=FALSE, include=FALSE}
PropertyLayer <- read.csv("file:///N:/KarlBlackhall/Gentrack AL/PROPERTY_LAYER_1516FY (Q1-Q4).csv",
                          stringsAsFactors = FALSE) %>%
                 mutate(ACC_NAME = gsub("[[:space:]]|[^[:alnum:]]", "", ACCOUNT_NAME))

KeyAccounts <- read.csv("file:///C:/Enquiries/data/KeyAccounts.csv",
                        stringsAsFactors = FALSE) %>%
               mutate(ACCOUNT_NAME = str_trim(gsub("(.+)(\\(.+)", "\\1", Key.Customer))) %>%
               select(ACCOUNT_NAME)


KeyAccountsName <- unique(gsub("[[:space:]]|[^[:alnum:]]", "", KeyAccounts$ACCOUNT_NAME))

link <- lapply(KeyAccountsName, function(x) PropertyLayer$MASTERID[which(grepl(x, PropertyLayer$ACC_NAME, ignore.case = TRUE) == TRUE)])

KeyAccountsID <- data.frame(MASTERID = unlist(link)) %>%
                 left_join(select(PropertyLayer, MASTERID, ACCOUNT_NAME)) %>%
                 distinct()

write.csv(KeyAccountsID, "C:/Enquiries/data/KeyAccountsID.csv")

KeyAccountsID <- read.csv("C:/Enquiries/data/KeyAccountsID.csv")

CallQual3$KEY_ACCOUNT <- "KEY_ACCOUNT"

CallQual3[!(as.numeric(substr(CallQual3$MEMO_CONSUMER, 3, 9)) %in% KeyAccountsID),]$KEY_ACCOUNT <- "NON_KEY"

```

```{r Gentrack Acc type, eval= eval_cell, message=FALSE, warning=FALSE, include=FALSE}

CallQual3$ACC_TYPE <- "TENANT"

CallQual3[substr(CallQual3$MEMO_CONSUMER, 1, 2) == 12,]$ACC_TYPE <- "OWNER"

CallQual3[substr(CallQual3$MEMO_CONSUMER, 1, 2) == 32,]$ACC_TYPE <- "TRADE_WASTE"

CallQual3[substr(CallQual3$MEMO_CONSUMER, 1, 2) == 99,]$ACC_TYPE <- "99"

CallQual3[substr(CallQual3$MEMO_CONSUMER, 1, 2) == 99,]$ACC_TYPE <- "99"

```

```{r Get gentack users report, eval=FALSE, include=FALSE}

getData <- function() {

  cmd <- readLines("N:/ABR/Output_2_RootCauseSRMandRepeats/SRSSreports/GetData.txt")

  # today <- format(Sys.Date(), "%d%m%Y")
  #
  # cmd <- gsub("(.*)(\\'\\D*)(\\d+)(.*\\')(.*)", paste0("\\1", "\\2", today, "\\4", ")"), cmd)

  shell(cmd, shell="C:/Windows/system32/cmd.exe")

}

getData()

```

```{r Gentrack Users, eval= eval_cell, include=FALSE}

Users <- read.csv("file:///N:/ABR/Output_2_RootCauseSRMandRepeats/SRSSreports/GentrackUsers.csv",
                  stringsAsFactors = FALSE) %>%
         select(USER_ID, FULL_NAME, ï..DEPARTMENT, Access)

CallQual3 <-   CallQual3 %>%
               left_join(Users, by = c("MEMO_CREATOR" = "USER_ID")) %>%
               left_join(Users, by = c("SR_CLOSER" = "USER_ID"))

colnames(CallQual3)[colnames(CallQual3) == "ï..DEPARTMENT.x"] <- "BEGIN"
colnames(CallQual3)[colnames(CallQual3) == "ï..DEPARTMENT.y"] <- "END"

```

```{r SRM, eval= eval_cell, include=FALSE}

CallQual3$SRM <- ifelse(!is.na(CallQual3$SR_SERV_CODE), "SRM", "RESOLVED")   

```

```{r Split into Customer and Memo tables, eval= eval_cell, include=FALSE}

Customer <- CallQual3 %>%
            select(1:6, USES, KEY_ACCOUNT, CUS_BIRTHDATE)

CallQual4 <- CallQual3 %>%
             select(1, USES, ACC_TYPE, MEMO_ID, MEMO_DATETIME, MEMO_CREATOR, FULL_NAME.x, BEGIN, Access.x, MEMO_TYPE, ENQUIRY, ACTION, RESULT, MEMO, SRM, SRM_ID, SR_DATETIME, SR_CREATOR, SR_CLOSER, FULL_NAME.y, END, Access.y, 27:34)

```

```{r PostgreSQL connect, message=FALSE, warning=FALSE, include=FALSE}

PostgreSQLconnect <- function(dbname = "ABRdb", type = 1, user = NULL, host = NULL) {

  if(!require(RPostgreSQL)) {
    message("installing the 'RPostgreSQL' package")
    install.packages("RPostgreSQL")
  }

  system("C:/bin/pgsql/run.bat")

  Sys.sleep(3)

  # Case 1: local database not requiring username/password
  if(type == 1) {

    con <- dbConnect(dbDriver("PostgreSQL"), dbname=dbname)
  }

  # Case 2: local database requiring username/password
  else if(type == 2) {

    con <- dbConnect(dbDriver("PostgreSQL"), user=user,
                     password=scan(what=character(),nmax=1,quiet=TRUE), dbname=dbname)
  }


  # Case 3: remote database requiring username/password
  else {
    con <- dbConnect(dbDriver("PostgreSQL"), user=user,
                     password=scan(what=character(),nmax=1,quiet=TRUE), dbname=dbname, host=host)
  }

  return(con)

}

conn <- PostgreSQLconnect()

```

```{r Write CAllQual3 to PGSQL, eval= eval_cell, message=FALSE, warning=FALSE, include=FALSE}

dbRemoveTable(conn, "CallQual_Memo")

dbWriteTable(con=conn,
             name="CallQual_Memo",
             value=CallQual4,
             row.names=FALSE,
             append=FALSE)

dbRemoveTable(conn, "CallQual_Customer")

dbWriteTable(con=conn,
             name="CallQual_Customer",
             value=Customer,
             row.names=FALSE,
             append=FALSE)

```

```{r Read in CallQual3, include=FALSE}

CallQual3 <- dbReadTable(con=conn,
                         name="CallQual_Memo")

CallQual_Customer <- dbReadTable(con=conn,
                         name="CallQual_Customer")
```


#Enquiries analysis {.tabset .tabset-fade}

## High level summary

```{r overall summary, message=FALSE, warning=FALSE, include=FALSE}

# x <- length(unique(CallQual3$MEMO_CONSUMER))

Filter <- ddply(CallQual3, .(ENQUIRY), summarise, Total = length(MEMO_CONSUMER)) %>%
                      arrange(-Total) %>%
                      mutate(cumulative = cumsum(Total)/sum(Total)) %>%
                      filter(cumulative < 0.93)

EnquiryCountAnnual <- CallQual3

EnquiryCountAnnual[!(EnquiryCountAnnual$ENQUIRY %in% Filter$ENQUIRY),]$ENQUIRY <- "OTHER"

EnquiryCountAnnual <- ddply(EnquiryCountAnnual, .(ENQUIRY, USES, SRM), summarise, Total = length(MEMO_CONSUMER)) %>%
                      arrange(-Total) %>%
                      select(USES,
                             SRM,
                             ENQUIRY,
                             Total)

```

There were `r sum(EnquiryCountAnnual$Total)` customer Enquiries logged in Gentrack between Jun 2014 and July 2016. This is broken down by year and into customer type in table 1 below.

```{r xtable1, echo=FALSE, results="asis"}

FY15 <- interval(ymd(20140701), ymd(20150630))
FY16 <- interval(ymd(20150701), ymd(20160630))
                                                             
CallQual3$FY <- ifelse(CallQual3$MEMO_DATETIME %within% FY15, 2015, 2016)

FYSummary <- ddply(CallQual3, .(FY, USES), summarise, Total = length(MEMO_CONSUMER)) %>%
             spread(USES, Total) %>%
             mutate(TotalEnquiries = NONRES + RES)

print(xtable(FYSummary), type = "html")


```

```{r Financial year + SRM summary, message=FALSE, warning=FALSE, include=FALSE}

FYSRMSummary <- ddply(CallQual3, .(FY, USES, SRM), summarise, Total = length(MEMO_CONSUMER)) %>%
             # spread(SRM, Total) %>%
             # mutate(TotalEnquiries = NONRES + RES)
                arrange(FY, USES, -Total)


```

\n 
`r sum(FYSRMSummary[FYSRMSummary$SRM == "SRM",]$Total)` enquiries, or `r paste(round(100 * sum(FYSRMSummary[FYSRMSummary$SRM == "SRM",]$Total)/ sum(FYSRMSummary$Total), 1), "%", sep="")` of all enquiries, resulted in an SRM being created between Jun 2014 and July 2016. 
\n 
As a group `r round(100 * sum(FYSRMSummary[FYSRMSummary$SRM == "SRM" & FYSRMSummary$USES == "NONRES", 4])/ sum(FYSRMSummary[FYSRMSummary$USES == "NONRES", 4]), 1)`% of all non-residential customers' enquiries resulted in an SRM between Jun 2014 and July 2016. This is compared to a rate of `r round(100 * sum(FYSRMSummary[FYSRMSummary$SRM == "SRM" & FYSRMSummary$USES == "RES", 4])/ sum(FYSRMSummary[FYSRMSummary$USES == "RES", 4]), 1)`% of residential enquiries generating an SRM over the same time period.   

```{r Plot1, eval=FALSE, message=FALSE, warning=FALSE, include=FALSE}

p1Annual <- ggplot(data = FYSRMSummary %>% arrange(-Total) %>% filter(SRM == "SRM"),
             aes(x = factor(USES),
                 fill= reorder(SRM, Total),
                 y = Total)) 

p1Annual <- p1Annual + geom_bar(stat="identity")

p1Annual <- p1Annual + facet_grid(facets=~FY)

p1Annual <- p1Annual + scale_y_continuous(labels = comma)

# p1Annual <- p1Annual + theme(axis.title.x=element_blank(),
#         axis.text.x=element_blank(),
#         axis.ticks.x=element_blank())

p1Annual <- p1Annual + labs(fill='SRM')

p1Annual

```

```{r Annual SRM summary, include=FALSE}

SRM_enquiry <- ddply(CallQual3 %>% filter(SRM == "SRM"), .(USES, ENQUIRY), summarise, Total = length(MEMO_CONSUMER)) %>%
                      arrange(-Total) #%>%
                      #mutate(cumulative = cumsum(Total)/sum(Total))# %>%
                      # filter(cumulative < 0.93)

SRM_enquiry_RES <- SRM_enquiry %>%
                   filter(USES == "RES") %>%
                   arrange(-Total) %>%
                   mutate(CumulativePercent = cumsum(Total)/sum(Total)) %>%
                   filter(CumulativePercent < 0.99) %>%
                   select(ENQUIRY, Total, CumulativePercent)

SRM_enquiry[SRM_enquiry$USES == "RES" & !(SRM_enquiry$ENQUIRY %in% SRM_enquiry_RES$ENQUIRY), ]$ENQUIRY <- "OTHER"

TopThree_RES <- SRM_enquiry_RES %>% 
                head(3) %>% 
                mutate(ENQUIRY = stri_trans_totitle(ENQUIRY)) %>% 
                .[["ENQUIRY"]]

SRM_enquiry_NRES <- SRM_enquiry%>%
                   filter(USES == "NONRES") %>%
                   arrange(-Total) %>%
                   mutate(CumulativePercent = cumsum(Total)/sum(Total)) %>%
                   filter(CumulativePercent < 0.99) %>%
                   select(ENQUIRY, Total, CumulativePercent)

SRM_enquiry[SRM_enquiry$USES == "NONRES" & !(SRM_enquiry$ENQUIRY %in% SRM_enquiry_NRES$ENQUIRY), ]$ENQUIRY <- "OTHER"

TopThree_NRES <- SRM_enquiry_NRES %>% 
                head(3) %>% 
                mutate(ENQUIRY = stri_trans_totitle(ENQUIRY)) %>% 
                .[["ENQUIRY"]]

SRM_enquiry <- aggregate(Total ~ USES + ENQUIRY, SRM_enquiry, sum)

SRM_enquiry <- SRM_enquiry %>%
               arrange(Total)



```

## Enquiry types

The graph and tables below show that the top three enquiry types (in order of importance) ending up as SRMs were `r TopThree_NRES[1:2]` and `r TopThree_NRES[3]` for non-residential as well as `r TopThree_RES[1:2]` and `r TopThree_RES[3]` for residential customers.   

```{r Annual SRM plots, echo=FALSE, message=FALSE, warning=FALSE}

# CallQual3$SRM <- ifelse(!is.na(CallQual3$SR_SERV_CODE), "SRM", "RESOLVED")   

# x <- length(unique(CallQual3$MEMO_CONSUMER))

SRM_enquiry$ENQUIRY <- factor(SRM_enquiry$ENQUIRY, levels = SRM_enquiry$ENQUIRY)

p1Annual <- ggplot(data = SRM_enquiry,
             aes(x = USES,
                 y = Total,
                 fill= reorder(ENQUIRY, Total)
                 )) 

p1Annual <- p1Annual + geom_bar(stat="identity")

# p1Annual <- p1Annual + theme(axis.title.x=element_blank(),
#         axis.text.x=element_blank(),
#         axis.ticks.x=element_blank())

#p1Annual <- p1Annual + facet_grid(facets=~FY)

p1Annual 

# p1Annual <- ggplot(data = EnquiryCountAnnual,
#              aes(x = factor(USES),
#                  fill= factor(ENQUIRY),
#                  y = Total)) 
# 
# p1Annual <- p1Annual + geom_bar(stat="identity")
# 
# p1Annual

# EnquiryCountAnnual <- CallQual3
# 
# EnquiryCountAnnual[!(EnquiryCountAnnual$ENQUIRY %in% Filter$ENQUIRY),]$ENQUIRY <- "OTHER"
# 
# EnquiryCountAnnual <- ddply(EnquiryCountAnnual, .(ENQUIRY, USES, SRM), summarise, Total = length(MEMO_CONSUMER)) %>%
#                       arrange(-Total) %>%
#                       select(USES,
#                              SRM,
#                              ENQUIRY,
#                              Total)

#Filter for SRM == TRUE

# Filter <- ddply(CallQual3 %>% filter(SRM == "SRM"), .(ENQUIRY), summarise, Total = length(MEMO_CONSUMER)/x) %>%
#                       arrange(-Total) %>%
#                       mutate(cumulative = cumsum(Total)/sum(Total)) %>%
#                       filter(cumulative < 0.93)
# 
# SRMCountAnnual <- CallQual3
# 
# SRMCountAnnual[!(SRMCountAnnual$ENQUIRY %in% Filter$ENQUIRY),]$ENQUIRY <- "OTHER"
# 
# SRMCountAnnual <- ddply(SRMCountAnnual %>% filter(SRM == "SRM"), .(USES, ENQUIRY), summarise, Total = length(MEMO_CONSUMER))  %>%
#                       #mutate(Total = 100 * Total/sum(Total)) %>% 
#                       arrange(USES, -Total)
# 
# p2Annual <- ggplot(data = SRMCountAnnual,
#              aes(x = factor(USES),
#                  fill= factor(ENQUIRY),
#                  y = Total)) 
# 
# p2Annual <- p2Annual + geom_bar(stat="identity")

#p2Annual <- p2Annual + scale_y_continuous(labels = percent)

#p2Annual <- p2Annual + facet_grid(facets=~USES)

# p2Annual

#
#p2Annual
#selectInput("p2", "", c("", ""))
```

## NON-RES Enquiry analysis

```{r xtable2, echo=FALSE, results="asis"}
      
print(xtable(SRM_enquiry_NRES, align = "cccr",latex.environments="center", format.args = list(digits = 2, format = c("d","d","s","f"))), type = "html", include.rownames=FALSE)

#print(xtable(m), add.to.row=list(list(1),"\\rowcolor[gray]{.8} "))
#print(xtable(SRM_enquiry_RES), type = "html")
```

## RES Enquiry analysis

```{r xtable3, echo=FALSE, results="asis"}

print(xtable(SRM_enquiry_RES, align = "cccr",latex.environments="center", format.args = list(digits = 2, format = c("d","d","s","f"))), type = "html", include.rownames=FALSE)

```


#Non-residential SRM analysis {.tabset .tabset-fade}

##Non-res customer analysis

```{r, include=FALSE}

SRM_NRES_type <- ddply(CallQual3 %>% filter(SRM == "SRM", USES == "NONRES"), .(ACC_TYPE, ENQUIRY, FY), summarise, Total = length(MEMO_CONSUMER)) %>%
                      arrange(-Total) #%>%
                      #mutate(cumulative = cumsum(Total)/sum(Total))# %>%
                      # filter(cumulative < 0.93)

SRM_NRES_type_filter <- aggregate(Total ~ ENQUIRY, SRM_NRES_type, sum)

SRM_NRES_type_filter <- SRM_NRES_type_filter %>%
                   arrange(-Total) %>%  
                   # group_by(ENQUIRY) %>%
                   # summarise(Total = sum(Total)) %>%
                   # ungroup %>%
                   mutate(CumulativePercent = cumsum(Total)/sum(Total)) %>%
                   filter(CumulativePercent < 0.99) %>%
                   select(ENQUIRY, Total, CumulativePercent)

SRM_NRES_type[!(SRM_NRES_type$ENQUIRY %in% SRM_NRES_type_filter$ENQUIRY), ]$ENQUIRY <- "OTHER"

SRM_NRES_type <- aggregate(Total ~ ACC_TYPE + ENQUIRY + FY, SRM_NRES_type, sum)

SRM_NRES_type <- SRM_NRES_type %>%
                 arrange(Total)

SRM_NRES_type$ENQUIRY <- factor(SRM_NRES_type$ENQUIRY, levels = unique(SRM_NRES_type$ENQUIRY))


```

```{r SRM by type, echo=FALSE}



renderPlot({p2 <- ggplot(data = SRM_NRES_type,
             aes(x = ACC_TYPE,
                 y = Total,
                 fill= reorder(ENQUIRY, Total),
                 order = -Total
                 )) 

p2 <- p2 + geom_bar(stat="identity")

p2 <- p2 + labs(fill = "ENQUIRY")

# p2 <- p2 + theme(axis.title.x=element_blank(),
#         axis.text.x=element_blank(),
#         axis.ticks.x=element_blank())

#p1Annual <- p1Annual + facet_grid(facets=~FY)

p2}) 

```

##Shiny

```{r, eval=FALSE, include=FALSE}
shinyApp(
  ui = fluidPage(
    selectInput("FY", label = "Financial year:", choices = c(2015, 2016, multiple=TRUE), selected = 2016),
    
    # sliderInput("amount_adjust", 
    #             label = "Amount",min = 1, max = 10, value = 1, step = 1),
    plotOutput("Enquirytype")
  ),
  server = function(input, output) {
    # set.seed(1234)
    # n <- 200
    # sdate <- as.POSIXct("2015-11-11 00:00:00",tz="UCT")
    # edate <- as.POSIXct("2015-11-11 23:59:59",tz="UCT")
    
    
    # d3 <- data.frame(
    #   ACC_TYPE =  SRM_NRES_type$ACC_TYPE,
    #   ENQUIRY = SRM_NRES_type$ENQUIRY,
    #   FY = SRM_NRES_type$FY,
    #   Total = SRM_NRES_type$Total
    
    d3 <- SRM_NRES_type 
    d3 <- d3[ order(d3$FY), ]
    
    output$Enquirytype <- renderPlot({
      d4 <- d3[ d3$FY==input$FY, ] 
      # d4$AdjAmount <- input$amount_adjust*d4$Amount
      ggplot(data=d4,aes(x = ACC_TYPE, y = Total, fill= reorder(ENQUIRY, Total))) + 
        geom_bar(stat="Identity") +
        labs(fill = "ENQUIRY")
    })
  },
  options = list(height = 800)
)
```

```{r echo = FALSE, eval=FALSE, include=FALSE}

selectInput("FY", label = "Financial year:", choices = c(2015, 2016, multiple=TRUE), selected = 2016)

```

```{r echo = FALSE, eval=FALSE, include=FALSE}

renderPlot({
      # d4 <- SRM_NRES_type[ SRM_NRES_type$FY==input$FY, ]
      # d4$AdjAmount <- input$amount_adjust*d4$Amount
      ggplot(data=SRM_NRES_type[ SRM_NRES_type$FY==input$FY, ],aes(x = ACC_TYPE, y = Total, fill= reorder(ENQUIRY, Total))) +
        geom_bar(stat="Identity") +
        labs(fill = "ENQUIRY")
    })

# renderPlot({
#       d3 <- data.frame(
#           ACC_TYPE =  SRM_NRES_type$ACC_TYPE,
#           ENQUIRY = SRM_NRES_type$ENQUIRY,
#           FY = SRM_NRES_type$FY,
#           Total = SRM_NRES_type$Total
#         )
#       d4 <- d3[ d3$FY==input$FY, ] 
#       # d4$AdjAmount <- input$amount_adjust*d4$Amount
#       ggplot(data=d4,aes(x = ACC_TYPE, y = Total, fill= reorder(ENQUIRY, Total))) + 
#         geom_bar(stat="Identity") +
#         labs(fill = "ENQUIRY")
#     })

```

```{r echo = FALSE, eval=FALSE, include=FALSE}

shinyApp(
  
  ui = fluidPage(
    selectInput("FY", label = "Financial year:", choices = c(2015, 2016, multiple=TRUE), selected = 2016),
    plotOutput("EnquiryPlot")
  ),
  
  server = function(input, output) {
    output$EnquiryPlot <- renderPlot({
      ggplot(data=SRM_NRES_type[ SRM_NRES_type$FY==input$FY, ],aes(x = ACC_TYPE, y = Total, fill= reorder(ENQUIRY, Total))) + 
        geom_bar(stat="Identity") +
        labs(fill = "ENQUIRY")
    })
  },
  
  options = list(height = 500)
)

```

```{r, echo = FALSE}

inputPanel(
  selectInput("FY", label = "Financial year:", choices = c(2015, 2016, multiple=TRUE), selected = 2016)
)

renderPlot({
  
  ggplot(data=SRM_NRES_type[ SRM_NRES_type$FY==input$FY, ],aes(x = ACC_TYPE, y = Total, fill= reorder(ENQUIRY, Total))) + 
         geom_bar(stat="Identity") +
         labs(fill = "ENQUIRY")
  # hist(faithful$eruptions, probability = TRUE, breaks = as.numeric(input$n_breaks),
  #      xlab = "Duration (minutes)", main = "Geyser eruption duration")
  # 
  # dens <- density(faithful$eruptions, adjust = input$bw_adjust)
  # lines(dens, col = "blue")
})
```

##Internal SRMs {.tabset .tabset-fade}

### Summary 

`r 100 * round(sum(SRM_enquiry_NRES[SRM_enquiry_NRES$ENQUIRY == "INTERNAL SRM", 2])/sum(SRM_enquiry_NRES[,2]), 2)`% of all non-residential SRMs are raised as Internal SRMs. 

```{r internal SRM and action, include=FALSE}

# CallQual3[CallQual3$SRM == TRUE,]$SRM <- "SRM"
# CallQual3[CallQual3$SRM == FALSE,]$SRM <- "RESOLVED"

InternalSRM_Action <- ddply(CallQual3 %>% filter(SRM == "SRM", USES == "NONRES", ENQUIRY == "INTERNAL SRM"), .(ACC_TYPE, ACTION), summarise, Total = length(MEMO_CONSUMER)) %>%
                      arrange(-Total) #%>%
                      #mutate(cumulative = cumsum(Total)/sum(Total))# %>%
                      # filter(cumulative < 0.93)

InternalSRM_Action_filter <- aggregate(Total ~ ACTION, InternalSRM_Action, sum)

InternalSRM_Action_filter <- InternalSRM_Action_filter %>%
                   arrange(-Total) %>%  
                   # group_by(ENQUIRY) %>%
                   # summarise(Total = sum(Total)) %>%
                   # ungroup %>%
                   mutate(CumulativePercent = cumsum(Total)/sum(Total)) %>%
                   filter(CumulativePercent < 0.99) %>%
                   select(ACTION, Total, CumulativePercent)

InternalSRM_Action[!(InternalSRM_Action$ACTION %in% InternalSRM_Action_filter$ACTION), ]$ACTION <- "OTHER"

InternalSRM_Action <- aggregate(Total ~ ACC_TYPE + ACTION, InternalSRM_Action, sum)

InternalSRM_Action <- InternalSRM_Action %>%
                      arrange(-Total)

# SRM_NRES_type$ENQUIRY <- factor(SRM_NRES_type$ENQUIRY, levels = unique(SRM_NRES_type$ENQUIRY))

```

These internal SRMs are raised against the tenant `r 100 * round(sum(InternalSRM_Action[InternalSRM_Action$ACC_TYPE == "TENANT", 3])/sum(InternalSRM_Action[,3]), 2)`% of the time followed by `r 100 * round(sum(InternalSRM_Action[InternalSRM_Action$ACC_TYPE == "OWNER", 3])/sum(InternalSRM_Action[,3]), 2)`% against the owner.   

```{r internal SRM contact type, include=FALSE}

InternalSRM_ConType <- ddply(CallQual3 %>% filter(SRM == "SRM", USES == "NONRES", ENQUIRY == "INTERNAL SRM"), .(SR_CALL_METHOD), summarise, Total = length(MEMO_CONSUMER)) %>%
                      arrange(-Total) %>%
                      mutate(percent = 100 * round(Total/sum(Total),2))

InternalSRM_ConType$SR_CALL_METHOD[InternalSRM_ConType$SR_CALL_METHOD == "I"] <- "Internal"
InternalSRM_ConType$SR_CALL_METHOD[InternalSRM_ConType$SR_CALL_METHOD == "P"] <- "Phone"
InternalSRM_ConType$SR_CALL_METHOD[InternalSRM_ConType$SR_CALL_METHOD == "E"] <- "Email"

Internal <- InternalSRM_ConType %>% filter(SR_CALL_METHOD == "Internal") %>% .[["percent"]]

TopThree_ACTION <- InternalSRM_ConType %>% filter(percent > 0, SR_CALL_METHOD != "Internal")

TopThree_ACTION <- paste(TopThree_ACTION[["SR_CALL_METHOD"]], paste("(", TopThree_ACTION[["percent"]], "%", ")", sep = ""))

```


The graph below shows `r Internal`% of Internal SRMs were generated internally with the majority of the remainder in response to `r TopThree_ACTION[1]` enquires. 

```{r internal SRM contact type plot, echo=FALSE}

p3 <- ggplot(data = InternalSRM_ConType,
             aes(x = factor(1),
                 y = Total,
                 fill = reorder(SR_CALL_METHOD, Total),
                 #order = Total
                 )) 

p3 <- p3 + geom_bar(stat="identity")

#p1Annual <- p1Annual + facet_grid(facets=~FY)

p3

```

```{r internal SRM, echo=FALSE}

pathway <- Enquiries::TeamSankey2(df = CallQual3, enquiry = "INTERNAL SRM", filename = "InternalSRM_Teamflow")

#Enquiries::TeamSankey(enquiry = "INTERNAL SRM", filename = "InternalSRM_Teamflow")

```

### SRM flow

The graph below shows that the most common pathways for Internal SRMs are:
* one `r pathway$Descr[1]` 
* two `r pathway$Descr[2]` 

```{r internal SRM sankey, echo=FALSE}

htmltools::includeHTML("C:/Enquiries/vignettes/InternalSRM_Teamflow.html")

```

```{r Top three actions, include=FALSE}
# 
# TopThree_ACTION <- InternalSRM_Action_filter %>% 
#                   head(3) %>% 
#                   mutate(ACTION = stri_trans_totitle(ACTION)) %>% 
#                   .[["ACTION"]]

TopThree_ACTION <- InternalSRM_Action_filter %>%  
                   mutate(percent = 100 * round(Total/sum(Total), 2)) %>%
                   head(3)

TopThree_ACTION <- paste(TopThree_ACTION[["ACTION"]], paste("(", TopThree_ACTION[["percent"]], "%", ")", sep = ""))

```

### SRM types

The graph show that the top three SRM types (in order of importance) raised for the enquiry type "Internal SRM" were `r TopThree_ACTION[1:2]` and `r TopThree_ACTION[3]`. 

```{r Action plot, echo=FALSE}

p4 <- ggplot(data = InternalSRM_Action,
             aes(x = factor(1),
                 y = Total,
                 fill= reorder(ACTION, Total),
                 order = Total
                 )) 

p4 <- p4 + geom_bar(stat="identity")

p4 <- p4 + theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())

p4 <- p4 + labs(fill='ENQUIRY')

#p1Annual <- p1Annual + facet_grid(facets=~FY)

p4

```



##Metering {.tabset .tabset-fade}

### Summary
`r 100 * round(sum(SRM_enquiry_NRES[SRM_enquiry_NRES$ENQUIRY == "METERING", 2])/sum(SRM_enquiry_NRES[,2]), 2)`% of all non-residential SRMs are raised as Metering SRMs. 

```{r Metering and action, include=FALSE}

# CallQual3[CallQual3$SRM == TRUE,]$SRM <- "SRM"
# CallQual3[CallQual3$SRM == FALSE,]$SRM <- "RESOLVED"

MeteringSRM_Action <- ddply(CallQual3 %>% filter(SRM == "SRM", USES == "NONRES", ENQUIRY == "METERING"), .(ACC_TYPE, ACTION), summarise, Total = length(MEMO_CONSUMER)) %>%
                      arrange(-Total) #%>%
                      #mutate(cumulative = cumsum(Total)/sum(Total))# %>%
                      # filter(cumulative < 0.93)

MeteringSRM_Action_filter <- aggregate(Total ~ ACTION, MeteringSRM_Action, sum)

MeteringSRM_Action_filter <- MeteringSRM_Action_filter %>%
                   arrange(-Total) %>%  
                   # group_by(ENQUIRY) %>%
                   # summarise(Total = sum(Total)) %>%
                   # ungroup %>%
                   mutate(CumulativePercent = cumsum(Total)/sum(Total)) %>%
                   filter(CumulativePercent < 0.99) %>%
                   select(ACTION, Total, CumulativePercent)

MeteringSRM_Action[!(MeteringSRM_Action$ACTION %in% MeteringSRM_Action_filter$ACTION), ]$ACTION <- "OTHER"

MeteringSRM_Action <- aggregate(Total ~ ACC_TYPE + ACTION, MeteringSRM_Action, sum)

MeteringSRM_Action <- MeteringSRM_Action %>%
                      arrange(-Total)

# SRM_NRES_type$ENQUIRY <- factor(SRM_NRES_type$ENQUIRY, levels = unique(SRM_NRES_type$ENQUIRY))

```

These Metering SRMs are raised against the owner `r 100 * round(sum(MeteringSRM_Action[MeteringSRM_Action$ACC_TYPE == "OWNER", 3])/sum(MeteringSRM_Action[,3]), 2)`% of the time followed by `r 100 * round(sum(MeteringSRM_Action[MeteringSRM_Action$ACC_TYPE == "TENANT", 3])/sum(MeteringSRM_Action[,3]), 2)`% against the tenant.   

```{r METERING SRM contact type, include=FALSE}

InternalSRM_ConType <- ddply(CallQual3 %>% filter(SRM == "SRM", USES == "NONRES", ENQUIRY == "METERING"), .(SR_CALL_METHOD), summarise, Total = length(MEMO_CONSUMER)) %>%
                      arrange(-Total) %>%
                      mutate(percent = 100 * round(Total/sum(Total),2))

InternalSRM_ConType$SR_CALL_METHOD[InternalSRM_ConType$SR_CALL_METHOD == "I"] <- "Internal"
InternalSRM_ConType$SR_CALL_METHOD[InternalSRM_ConType$SR_CALL_METHOD == "P"] <- "Phone"
InternalSRM_ConType$SR_CALL_METHOD[InternalSRM_ConType$SR_CALL_METHOD == "E"] <- "Email"

Internal <- InternalSRM_ConType %>% filter(SR_CALL_METHOD == "Internal") %>% .[["percent"]]

TopThree_ACTION <- InternalSRM_ConType %>% filter(percent > 0, SR_CALL_METHOD != "Internal")

TopThree_ACTION <- paste(TopThree_ACTION[["SR_CALL_METHOD"]], paste("(", TopThree_ACTION[["percent"]], "%", ")", sep = ""))

```

The graph below shows `r Internal`% of metering SRMs were generated internally with the majority of the remainder in response to `r TopThree_ACTION[1]` enquires. 

```{r METERING contact type plot, echo=FALSE}

p5 <- ggplot(data = InternalSRM_ConType,
             aes(x = factor(1),
                 y = Total,
                 fill= reorder(SR_CALL_METHOD, Total),
                 order = Total
                 )) 

p5 <- p5 + geom_bar(stat="identity")

p5 <- p5 + theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())

p5 <- p5 + labs(fill='CONTACT METHOD')

#p1Annual <- p1Annual + facet_grid(facets=~FY)

p5

```

```{r Metering SRM, include=FALSE}

pathway <- Enquiries::TeamSankey2(df = CallQual3, enquiry = "METERING", filename = "MeteringSRM_Teamflow")

```

### SRM flow

The graph below shows that the most common pathways for Internal SRMs are:
* `r pathway$Descr[1]` 
* `r pathway$Descr[2]`

```{r Metering SRM sankey, echo=FALSE}

# Enquiries::TeamSankey(enquiry = "METERING", filename = "MeteringSRM_Teamflow")

htmltools::includeHTML("C:/Enquiries/vignettes/MeteringSRM_Teamflow.html")

```

```{r Top three actions Metering, include=FALSE}

TopThree_ACTION <- MeteringSRM_Action_filter %>%  
                   mutate(percent = 100 * round(Total/sum(Total), 2)) %>%
                   head(3)

TopThree_ACTION <- paste(TopThree_ACTION[["ACTION"]], paste("(", TopThree_ACTION[["percent"]], "%", ")", sep = ""))

```

### SRM types

The graph show that the top three SRM types (in order of importance) raised for the enquiry type "Metering" were `r TopThree_ACTION[1:2]` and `r TopThree_ACTION[3]`. 

```{r Action plot Metering, echo=FALSE}

p4 <- ggplot(data = MeteringSRM_Action,
             aes(x = factor(1),
                 y = Total,
                 fill= reorder(ACTION, Total),
                 order = Total
                 )) 

p4 <- p4 + geom_bar(stat="identity")

p4 <- p4 + theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())

p4 <- p4 + labs(fill='ENQUIRY')

#p1Annual <- p1Annual + facet_grid(facets=~FY)

p4

```




##Trade Waste {.tabset .tabset-fade}

### Summary
`r 100 * round(sum(SRM_enquiry_NRES[SRM_enquiry_NRES$ENQUIRY == "TRADE WASTE", 2])/sum(SRM_enquiry_NRES[,2]), 2)`% of all non-residential SRMs are raised as Trade waste SRMs. 

```{r Trade Waste and action, include=FALSE}

# CallQual3[CallQual3$SRM == TRUE,]$SRM <- "SRM"
# CallQual3[CallQual3$SRM == FALSE,]$SRM <- "RESOLVED"

TradeWasteSRM_Action <- ddply(CallQual3 %>% filter(SRM == "SRM", USES == "NONRES", ENQUIRY == "TRADE WASTE"), .(ACC_TYPE, ACTION), summarise, Total = length(MEMO_CONSUMER)) %>%
                      arrange(-Total) #%>%
                      #mutate(cumulative = cumsum(Total)/sum(Total))# %>%
                      # filter(cumulative < 0.93)

TradeWasteSRM_Action_filter <- aggregate(Total ~ ACTION, TradeWasteSRM_Action, sum)

TradeWasteSRM_Action_filter <- TradeWasteSRM_Action_filter %>%
                   arrange(-Total) %>%  
                   # group_by(ENQUIRY) %>%
                   # summarise(Total = sum(Total)) %>%
                   # ungroup %>%
                   mutate(CumulativePercent = cumsum(Total)/sum(Total)) %>%
                   filter(CumulativePercent < 0.99) %>%
                   select(ACTION, Total, CumulativePercent)

TradeWasteSRM_Action[!(TradeWasteSRM_Action$ACTION %in% TradeWasteSRM_Action_filter$ACTION), ]$ACTION <- "OTHER"

TradeWasteSRM_Action <- aggregate(Total ~ ACC_TYPE + ACTION, TradeWasteSRM_Action, sum)

TradeWasteSRM_Action <- TradeWasteSRM_Action %>%
                        arrange(-Total)

# SRM_NRES_type$ENQUIRY <- factor(SRM_NRES_type$ENQUIRY, levels = unique(SRM_NRES_type$ENQUIRY))

```

These internal SRMs are raised against the trade waste account `r 100 * round(sum(TradeWasteSRM_Action[TradeWasteSRM_Action$ACC_TYPE == "TRADE_WASTE", 3])/sum(TradeWasteSRM_Action[,3]), 2)`% of the time followed by `r 100 * round(sum(TradeWasteSRM_Action[TradeWasteSRM_Action$ACC_TYPE == "TENANT", 3])/sum(TradeWasteSRM_Action[,3]), 2)`% against the tenant.   

```{r TRADEWASTE SRM contact type, include=FALSE}

InternalSRM_ConType <- ddply(CallQual3 %>% filter(SRM == "SRM", USES == "NONRES", ENQUIRY == "TRADE WASTE"), .(SR_CALL_METHOD), summarise, Total = length(MEMO_CONSUMER)) %>%
                      arrange(-Total) %>%
                      mutate(percent = 100 * round(Total/sum(Total),2))

InternalSRM_ConType$SR_CALL_METHOD[InternalSRM_ConType$SR_CALL_METHOD == "I"] <- "Internal"
InternalSRM_ConType$SR_CALL_METHOD[InternalSRM_ConType$SR_CALL_METHOD == "P"] <- "Phone"
InternalSRM_ConType$SR_CALL_METHOD[InternalSRM_ConType$SR_CALL_METHOD == "E"] <- "Email"

Internal <- InternalSRM_ConType %>% filter(SR_CALL_METHOD == "Internal") %>% .[["percent"]]

TopThree_ACTION <- InternalSRM_ConType %>% filter(percent > 0, SR_CALL_METHOD != "Internal")

TopThree_ACTION <- paste(TopThree_ACTION[["SR_CALL_METHOD"]], paste("(", TopThree_ACTION[["percent"]], "%", ")", sep = ""))

```

The graph below shows `r Internal`% of trade waste SRMs were generated internally with the majority of the remainder in response to `r TopThree_ACTION[1]` enquires. 

```{r TRADEWASTE contact type plot, echo=FALSE}

p6 <- ggplot(data = InternalSRM_ConType,
             aes(x = factor(1),
                 y = Total,
                 fill= reorder(SR_CALL_METHOD, Total),
                 order = Total
                 )) 

p6 <- p6 + geom_bar(stat="identity")

p6 <- p6 + theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())

p6 <- p6 + labs(fill='CONTACT METHOD')
#p1Annual <- p1Annual + facet_grid(facets=~FY)

p6

```

```{r TRADEWASTE SRM, include=FALSE}

pathway <- Enquiries::TeamSankey2(df = CallQual3, enquiry = "TRADE WASTE", filename = "TradeWasteSRM_Teamflow")

```
### SRM flow
The graph below shows that the most common pathways for Internal SRMs are:
* `r pathway$Descr[1]` 
* `r pathway$Descr[2]`
 

```{r TRADEWASTE SRM sankey, echo=FALSE}

# Enquiries::TeamSankey(enquiry = "TRADE WASTE", filename = "TradeWasteSRM_Teamflow")

htmltools::includeHTML("C:/Enquiries/vignettes/TradeWasteSRM_Teamflow.html")

```

```{r Top three actions Trade Waste, echo=FALSE}

TopThree_ACTION <- TradeWasteSRM_Action_filter %>%  
                   mutate(percent = 100 * round(Total/sum(Total), 2)) %>%
                   head(3)

TopThree_ACTION <- paste(TopThree_ACTION[["ACTION"]], paste("(", TopThree_ACTION[["percent"]], "%", ")", sep = ""))

```

### SRM types

The graph show that the top three SRM types (in order of importance) raised for the enquiry type "Trade waste" were `r TopThree_ACTION[1:2]` and `r TopThree_ACTION[3]`. 

```{r Action plot Trade Waste, echo=FALSE}

p5 <- ggplot(data = TradeWasteSRM_Action,
             aes(x = factor(1),
                 y = Total,
                 fill= reorder(ACTION, Total),
                 order = Total
                 )) 

p5 <- p5 + geom_bar(stat="identity")

p5 <- p5 + theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())

p5 <- p5 + labs(fill='ENQUIRY')

#p1Annual <- p1Annual + facet_grid(facets=~FY)

p5

```


The graph below shows over `r 2 + 2` percent of all customer enquiries between Jun 2014 and July 2016 were resolved at first point of contact. Approximately X percent of all customer enquiries were from residential type customers. 

```{r Sankey graph, eval=FALSE, message=FALSE, warning=FALSE, include=FALSE}

sankeyPlot <- function(df, name){
  sankeyPlot <- NULL
  sankeyPlot <- rCharts$new()    #We need to tell R where the Sankey library is.  #I put it as a subdirectory to my current working directory (.)
  sankeyPlot$setLib('http://timelyportfolio.github.io/rCharts_d3_sankey')    #We also need to point to an HTML template page
  sankeyPlot$setTemplate(script =  "http://timelyportfolio.github.io/rCharts_d3_sankey/layouts/chart.html")
  sankeyPlot$set(
    data = df,
    nodeWidth = 15,
    nodePadding = 10,
    layout = 32,
    width = 750,
    height = 500,
    labelFormat = ".1%"
  )
  sankeyPlot$save(paste(name, '.html', sep = ""))}

EnquiryCountAnnual <- ddply(CallQual3, .(ENQUIRY, USES, SRM), summarise, Total = length(MEMO_CONSUMER)) %>%
                      arrange(-Total) %>%
                      select(USES,
                             SRM,
                             ENQUIRY,
                             Total)

Filter <- ddply(CallQual3 %>% filter(SRM == "SRM"), .(ENQUIRY), summarise, Total = length(MEMO_CONSUMER)/x) %>%
                      arrange(-Total) %>%
                      mutate(cumulative = cumsum(Total)/sum(Total)) %>%
                      filter(cumulative < 0.93)

x <- length(unique(CallQual3$MEMO_CONSUMER))

EnquiryCountAnnual_sankey <- EnquiryCountAnnual

EndUse_enquiry <- aggregate(Total ~ USES + ENQUIRY, EnquiryCountAnnual, sum) %>%
                  mutate(Total = Total/sum(Total))

colnames(EndUse_enquiry) <- c("source", "target", "value")

Enquiry_SRM <- aggregate(Total ~ ENQUIRY + SRM, EnquiryCountAnnual, sum) %>%
                  mutate(Total = Total/sum(Total))

colnames(Enquiry_SRM) <- c("source", "target", "value")

Enduse_SRM = rbind(EndUse_enquiry, Enquiry_SRM)

#d <- data.frame(
  #id = grant_id, 
  #source = funding_agency, 
  #target = study_section, 
  #value = total_cost
#)
#devtools::install_github("rCharts", "ramnathv", ref = "dev")

sankeyPlot(Enduse_SRM, name = "Enduse_SRM")

htmltools::includeHTML("C:/Enquiries/data/Enduse_SRM.html")


```

Over 40,000 enquiries between Jun 2014 and July 2016 


```{r Non-res SRM flow, eval = FALSE, echo=FALSE, message=FALSE, warning=FALSE}

NONRES_SRM <- CallQual3 %>% filter(SRM == "SRM", USES == "NONRES")
# 
# Users <- read.csv("file:///N:/ABR/Output_2_RootCauseSRMandRepeats/SRSSreports/GentrackUsers.csv",
#                   stringsAsFactors = FALSE) %>%
#          select(USER_ID, FULL_NAME, ï..DEPARTMENT, Access)
# 
# NONRES_SRM <- NONRES_SRM %>%
#                left_join(Users, by = c("MEMO_CREATOR" = "USER_ID")) %>%
#                left_join(Users, by = c("SR_CLOSER" = "USER_ID"))

Filter <- ddply(NONRES_SRM, .(ENQUIRY), summarise, Total = length(MEMO_CONSUMER)) %>%
                      arrange(-Total) %>%
                      mutate(cumulative = cumsum(Total)/sum(Total)) %>%
                      filter(cumulative < 0.93)

Filter2 <- ddply(NONRES_SRM, .(SOTDESCRIPTION), summarise, Total = length(MEMO_CONSUMER)) %>%
                      arrange(-Total) %>%
                      mutate(cumulative = cumsum(Total)/sum(Total)) %>%
                      filter(cumulative < 0.9)

SRMCountAnnual <- NONRES_SRM

SRMCountAnnual[!(SRMCountAnnual$ENQUIRY %in% Filter$ENQUIRY),]$ENQUIRY <- "OTHER_ENQUIRY"

SRMCountAnnual[!(SRMCountAnnual$SOTDESCRIPTION %in% Filter2$SOTDESCRIPTION),]$SOTDESCRIPTION <- "OTHER_SRM"

SRM2 <- ddply(SRMCountAnnual, .(USES, ACC_TYPE, `ï..DEPARTMENT.x`, `ï..DEPARTMENT.y`, SR_CALL_METHOD, ENQUIRY, SOTDESCRIPTION, SR_CLOSER), summarise, Total = length(MEMO_CONSUMER)) %>% filter(complete.cases(.))

# x <- length(unique(filter(SRMCountAnnual, SRM == "SRM")$MEMO_CONSUMER))

USES_TYPE <- aggregate(Total ~ USES + ACC_TYPE, SRM2, sum) %>%
                          mutate(Total = Total/sum(Total))

colnames(USES_TYPE) <- c("source", "target", "value")

USES_METHOD <- aggregate(Total ~ ACC_TYPE + SR_CALL_METHOD, SRM2, sum) %>%
                          mutate(Total = Total/sum(Total))

colnames(USES_METHOD) <- c("source", "target", "value")

Enquiry_SRM <- aggregate(Total ~ SR_CALL_METHOD + ENQUIRY, SRM2, sum) %>%
                          mutate(Total = Total/sum(Total))

colnames(Enquiry_SRM) <- c("source", "target", "value")

sankeyPlot(Enquiry_SRM, "Enquiry_SRM")

Enquiry_SOT <- aggregate(Total ~ ENQUIRY + SOTDESCRIPTION, SRM2, sum) %>%
                          mutate(Total = Total/sum(Total))

colnames(Enquiry_SOT) <- c("source", "target", "value")

sankeyPlot(Enquiry_SOT, "Enquiry_SOT")

SOT_CLOSER <- aggregate(Total ~ SOTDESCRIPTION + SR_CLOSER, SRM2, sum) %>%
                          mutate(Total = Total/sum(Total))

colnames(SOT_CLOSER) <- c("source", "target", "value")

SOT = rbind(Enquiry_SRM, USES_TYPE, USES_METHOD, Enquiry_SOT) 

sankeyPlot(SOT, "Enquiry_SOT")

htmltools::includeHTML("C:/Enquiries/data/Enquiry_SOT.html")

```

```{r Gentrack users Sankey, eval=FALSE, include=FALSE, echo=FALSE}

Enquiry_Creator <- aggregate(Total ~ SR_CALL_METHOD + `ï..DEPARTMENT.x`, SRM2, sum) %>%
                          mutate(Total = Total/sum(Total))

colnames(Enquiry_Creator) <- c("source", "target", "value")

Creator_Closer <- aggregate(Total ~ `ï..DEPARTMENT.x` + `ï..DEPARTMENT.y`, SRM2, sum) %>%
                           mutate(Total = Total/sum(Total),
                                  `ï..DEPARTMENT.y` = paste(`ï..DEPARTMENT.y`, "_end"))
 
colnames(Creator_Closer) <- c("source", "target", "value")

# Creator_Enquiry <- aggregate(Total ~ `ï..DEPARTMENT.x` + ENQUIRY, SRM2, sum) %>%
#                           mutate(Total = Total/sum(Total))
# 
# colnames(Creator_Enquiry) <- c("source", "target", "value")

# Enquiry_Closer <-  aggregate(Total ~ ENQUIRY + `ï..DEPARTMENT.y`, SRM2, sum) %>%
#                           mutate(Total = Total/sum(Total),
#                                  `ï..DEPARTMENT.y` = paste(`ï..DEPARTMENT.y`, "_end"))
# 
# colnames(Enquiry_Closer) <- c("source", "target", "value")

#Users = rbind(USES_TYPE, USES_METHOD, Enquiry_Creator, Creator_Enquiry,  Enquiry_Closer)

Users = rbind(USES_TYPE, USES_METHOD, Enquiry_Creator, Creator_Closer)

sankeyPlot(Users, "Enquiry_users")

htmltools::includeHTML("C:/Enquiries/data/Enquiry_users.html")

```

```{r Gentrack users Sankey - Internal removed, eval=FALSE, include=FALSE, echo=FALSE}

Users2 = rbind(USES_TYPE, USES_METHOD, Enquiry_Creator, Creator_Closer) %>%
         filter(source != "I", target != "I")

sankeyPlot(Users2, "Enquiry_users2")

htmltools::includeHTML("C:/Enquiries/data/Enquiry_users2.html")

```

