---
title: "Internal SRM analysis"
author: "Phil Farrell"
date: "1 March 2017"
output:
  html_document: default
  pdf_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r setup script, message=FALSE, warning=FALSE, include=FALSE}

#setwd("C:/Enquiries")
knitr::opts_chunk$set(echo = TRUE)

packages <- c("readr", "dplyr", "plyr", "tidyr", "ggplot2", "stringr", "lubridate", "sqldf", "randomNames", "data.table", "devtools", "scales", "knitr", "xtable", "stringi", "shiny", "zoo", "pMineR", "edeaR", "Rcpp")

p <- installed.packages()
# 
# ifelse(length(packages[!(packages %in% row.names(p))]) > 0,
#install.packages(pkgs = packages[!(packages %in% row.names(p))])#, repos = "https://cran.ms.unimelb.edu.au/", print("OK"))



library(devtools)

ifelse(!("rCharts" %in% row.names(p)), install_github('ramnathv/rCharts'), TRUE)

#library(Enquiries)
#library(ABR)
library(rCharts)

lapply(packages, require, character.only = TRUE)

```

```{r PostgreSQL connect, message=FALSE, warning=FALSE, include=FALSE}

PostgreSQLconnect <- function(dbname = "ABRdb", type = 1, user = NULL, host = NULL) {

  if(!require(RPostgreSQL)) {
    message("installing the 'RPostgreSQL' package")
    install.packages("RPostgreSQL", repos = "https://cran.ms.unimelb.edu.au/")
  }

  system("C:/Users/farrelp1/Documents/bin/pgsql/run.bat")

  Sys.sleep(3)

  # Case 1: local database not requiring username/password
  if(type == 1) {

    con <- dbConnect(dbDriver("PostgreSQL"), dbname=dbname)
  }

  # Case 2: local database requiring username/password
  else if(type == 2) {

    con <- dbConnect(dbDriver("PostgreSQL"), user=user,
                     password=scan(what=character(),nmax=1,quiet=TRUE), dbname=dbname)
  }


  # Case 3: remote database requiring username/password
  else {
    con <- dbConnect(dbDriver("PostgreSQL"), user=user,
                     password=scan(what=character(),nmax=1,quiet=TRUE), dbname=dbname, host=host)
  }

  return(con)

}

conn <- PostgreSQLconnect()

```

```{r Read in CallQual3, include=FALSE}

CallQual3 <- dbReadTable(con=conn,
                         name="CallQual_Memo")

CallQual_Customer <- dbReadTable(con=conn,
                         name="CallQual_Customer")
```

```{r Date timev2, message=FALSE, warning=FALSE, include=FALSE}

CallQual3 <- CallQual3 %>%
                    mutate(SRM = ifelse(!is.na(CallQual3$SR_SERV_CODE), "SRM", "RESOLVED"),
                    MEMO_DATETIME = parse_date_time(MEMO_DATETIME, orders="%y-%m-%d %H:%M:%S"),
                    SR_DATETIME = parse_date_time(SR_DATETIME, orders="%y-%m-%d %H:%M:%S"),
                    STAT_DATE = dmy(format(STAT_DATE, format="%d/%m/%y")))

```

```{r xtable1, include=FALSE, results="asis"}

CallQual3$FY <- ifelse(CallQual3$MEMO_DATETIME < ymd("20150701"), 2015, 2016)

FYSummary <- ddply(CallQual3, .(FY, USES), summarise, Total = length(MEMO_CONSUMER)) %>%
             spread(USES, Total) %>%
             mutate(TotalEnquiries = NONRES + RES)

```

```{r, include=FALSE}

getYearQuarter <- function(x, 
                           firstMonth=7, 
                           fy.prefix='FY', 
                           quarter.prefix='Q',
                           sep='-',
                           level.range=c(min(x), max(x)) ) {
  if(level.range[1] > min(x) | level.range[2] < max(x)) {
    warning(paste0('The range of x is greater than level.range. Values ',
                   'outside level.range will be returned as NA.'))
  }
  quarterString <- function(d) {
    year <- as.integer(format(d, format='%Y'))
    month <- as.integer(format(d, format='%m'))
    y <- ifelse(firstMonth > 1 & month >= firstMonth, year+1, year)  
    q <- cut( (month - firstMonth) %% 12, breaks=c(-Inf,2,5,8,Inf), 
              labels=paste0(quarter.prefix, 1:4))
    return(paste0(fy.prefix, y, sep, q))
  }
  vals <- quarterString(x)
  levels <- unique(quarterString(seq(
    as.Date(format(level.range[1], '%Y-%m-01')), 
    as.Date(format(level.range[2], '%Y-%m-28')), by='month')))
  return(factor(vals, levels=levels, ordered=TRUE))
}

# CallQual3$MONTH <- lubridate::month(CallQual3$MEMO_DATETIME, label = TRUE)
CallQual3$MONTH <- format(CallQual3$MEMO_DATETIME, "%Y-%m")
# CallQual3$MONTH <- as.Date(CallQual3$MEMO_DATETIME, format = "%m-%Y")
# CallQual3$MONTH <- as.yearmon(CallQual3$MEMO_DATETIME)
# CallQual3$QUARTER <- quarter(CallQual3$MEMO_DATETIME)
# CallQual3$QUARTER <- lubridate::quarter(CallQual3$MEMO_DATETIME, with_year = TRUE)

CallQual3$QUARTER <- getYearQuarter(CallQual3$MEMO_DATETIME)

SRM_NRES_type <- ddply(CallQual3 %>% filter(SRM == "SRM", USES == "NONRES"), .(ACC_TYPE, ENQUIRY, MONTH, QUARTER, FY), summarise, Total = length(MEMO_CONSUMER)) %>%
                      arrange(-Total)

# SRM_NRES_type <- ddply(CallQual3 %>% filter(SRM == "SRM", USES == "NONRES"), .(ACC_TYPE, ENQUIRY, FY), summarise, Total = length(MEMO_CONSUMER)) %>%
#                       arrange(-Total) #%>%
                      #mutate(cumulative = cumsum(Total)/sum(Total))# %>%
                      # filter(cumulative < 0.93)

SRM_NRES_type_filter <- aggregate(Total ~ ENQUIRY, SRM_NRES_type, sum)

SRM_NRES_type_filter <- SRM_NRES_type_filter %>%
                   arrange(-Total) %>%  
                   # group_by(ENQUIRY) %>%
                   # summarise(Total = sum(Total)) %>%
                   # ungroup %>%
                   mutate(CumulativePercent = cumsum(Total)/sum(Total)) %>%
                   filter(CumulativePercent < 0.99) %>%
                   dplyr::select(ENQUIRY, Total, CumulativePercent)

SRM_NRES_type[!(SRM_NRES_type$ENQUIRY %in% SRM_NRES_type_filter$ENQUIRY), ]$ENQUIRY <- "OTHER"

SRM_NRES_type <- aggregate(Total ~ ACC_TYPE + ENQUIRY + MONTH + QUARTER + FY, SRM_NRES_type, sum)

SRM_NRES_type <- SRM_NRES_type %>%
                 arrange(Total)

SRM_NRES_type$ENQUIRY <- factor(SRM_NRES_type$ENQUIRY, levels = unique(SRM_NRES_type$ENQUIRY))

SRM_NRES_type <- SRM_NRES_type %>%
                 gather(XAXIS, VALUE, ACC_TYPE, MONTH:QUARTER)

```

#Summary

```{r Annual SRM summary, include=FALSE}

SRM_enquiry <- ddply(CallQual3 %>% filter(SRM == "SRM"), .(USES, ENQUIRY), summarise, Total = length(MEMO_CONSUMER)) %>%
                      arrange(-Total) #%>%
                      #mutate(cumulative = cumsum(Total)/sum(Total))# %>%
                      # filter(cumulative < 0.93)

SRM_enquiry_RES <- SRM_enquiry %>%
                   filter(USES == "RES") %>%
                   arrange(-Total) %>%
                   mutate(CumulativePercent = cumsum(Total)/sum(Total),
                          Percent = 100 * Total/sum(Total)) %>%
                   filter(CumulativePercent < 0.99) %>%
                   dplyr::select(ENQUIRY, Total, CumulativePercent, Percent)

SRM_enquiry[SRM_enquiry$USES == "RES" & !(SRM_enquiry$ENQUIRY %in% SRM_enquiry_RES$ENQUIRY), ]$ENQUIRY <- "OTHER"

TopThree_RES <- SRM_enquiry_RES %>% 
                head(3) %>% 
                mutate(ENQUIRY = stri_trans_totitle(ENQUIRY)) %>% 
                .[["ENQUIRY"]]

SRM_enquiry_NRES <- SRM_enquiry%>%
                   filter(USES == "NONRES") %>%
                   arrange(-Total) %>%
                   mutate(CumulativePercent = cumsum(Total)/sum(Total),
                          Percent = 100 * Total/sum(Total)) %>%
                   filter(CumulativePercent < 0.99) %>%
                   dplyr::select(ENQUIRY, Total, CumulativePercent, Percent)

SRM_enquiry[SRM_enquiry$USES == "NONRES" & !(SRM_enquiry$ENQUIRY %in% SRM_enquiry_NRES$ENQUIRY), ]$ENQUIRY <- "OTHER"

TopThree_NRES <- SRM_enquiry_NRES %>% 
                head(3) %>% 
                mutate(ENQUIRY = stri_trans_totitle(ENQUIRY)) %>% 
                .[["ENQUIRY"]]

SRM_enquiry <- aggregate(Total ~ USES + ENQUIRY, SRM_enquiry, sum)

SRM_enquiry <- SRM_enquiry %>%
               arrange(Total)



```

`r 100 * round(sum(SRM_enquiry_NRES[SRM_enquiry_NRES$ENQUIRY == "INTERNAL SRM", 2])/sum(SRM_enquiry_NRES[,2]), 2)` percent of all non-residential SRMs generated were labelled as "Internal SRMs" by contact centre staff.

```{r internal SRM and action, include=FALSE}

# CallQual3[CallQual3$SRM == TRUE,]$SRM <- "SRM"
# CallQual3[CallQual3$SRM == FALSE,]$SRM <- "RESOLVED"

InternalSRM_Action <- ddply(CallQual3 %>% filter(SRM == "SRM", USES == "NONRES", ENQUIRY == "INTERNAL SRM"), .(FY, QUARTER, MONTH, ACC_TYPE, ACTION), summarise, Total = length(MEMO_CONSUMER)) %>%
                      arrange(-Total) #%>%
                      #mutate(cumulative = cumsum(Total)/sum(Total))# %>%
                      # filter(cumulative < 0.93)

InternalSRM_Action_filter <- aggregate(Total ~ ACTION, InternalSRM_Action, sum)

InternalSRM_Action_filter <- InternalSRM_Action_filter %>%
                   arrange(-Total) %>%  
                   # group_by(ENQUIRY) %>%
                   # summarise(Total = sum(Total)) %>%
                   # ungroup %>%
                   mutate(CumulativePercent = cumsum(Total)/sum(Total)) %>%
                   filter(CumulativePercent < 0.99) %>%
                   dplyr::select(ACTION, Total, CumulativePercent)

InternalSRM_Action[!(InternalSRM_Action$ACTION %in% InternalSRM_Action_filter$ACTION), ]$ACTION <- "OTHER"

InternalSRM_Action <- aggregate(Total ~ FY + QUARTER + MONTH + ACC_TYPE + ACTION, InternalSRM_Action, sum)

InternalSRM_Action <- InternalSRM_Action %>%
                      arrange(-Total)

InternalSRM_Action <- InternalSRM_Action %>%
                       gather(XAXIS, VALUE, ACC_TYPE, QUARTER:MONTH)

# SRM_NRES_type$ENQUIRY <- factor(SRM_NRES_type$ENQUIRY, levels = unique(SRM_NRES_type$ENQUIRY))

```

```{r Top three actions, include=FALSE}
# 
# TopThree_ACTION <- InternalSRM_Action_filter %>% 
#                   head(3) %>% 
#                   mutate(ACTION = stri_trans_totitle(ACTION)) %>% 
#                   .[["ACTION"]]

TopThree_ACTION <- InternalSRM_Action_filter %>%  
                   mutate(percent = 100 * round(Total/sum(Total), 2)) %>%
                   head(3)

TopThree_ACTION <- paste(TopThree_ACTION[["ACTION"]], paste("(", TopThree_ACTION[["percent"]], "%", ")", sep = ""))

```

The top three SRM types (in order of importance) raised for the enquiry type "Internal SRM" were `r TopThree_ACTION[1:2]` and `r TopThree_ACTION[3]`. 

```{r Action 2 Shiny, include=FALSE}

Exceptions <- c("Kate Do", "Christine Mallia", "Rachel Hales", "Jimelyn De Guzman", "Lindsay Burke", "Zita Alderson")

unique(CallQual3$MEMO_CREATOR[CallQual3$ENQUIRY == "INTERNAL SRM" & is.na(CallQual3$FULL_NAME.x) & !(CallQual3$FULL_NAME.x %in% Exceptions)])

Supply <- c("Linda Shanks", "Veronica Vasjuta", "Kim Junker", "Chanel Dennis")

Audits <- c("Anuj Bhatnagar", "Natasha Sfetkas")

ActionType <- function(FULL_NAME = FULL_NAME.x, ENQUIRY = ENQUIRY, ACTION = ACTION) {
  
  if(ENQUIRY == "INTERNAL SRM") {
    
    if(FULL_NAME %in% Exceptions) {
      
      return(paste0("EXCEPTIONS", "-", ACTION))
      
    }
    
    if(FULL_NAME %in% Supply) {
      
      return(paste0("SUPPLY", "-", ACTION))
      
    }
    
    if(FULL_NAME %in% Audits) {
      
      return(paste0("AUDITS", "-", ACTION))
      
    }
    
    else {
      
      return(ACTION)
      
    }
    
  }
  
  else {
    
    return(ACTION)
    
  }
  
}

ActionType <- Vectorize(ActionType)

InternalSRM_Action2 <- ddply(CallQual3 %>% filter(SRM == "SRM", USES == "NONRES", ENQUIRY == "INTERNAL SRM"), .(FY, QUARTER, MONTH, ACC_TYPE, ACTION, ENQUIRY, FULL_NAME.x), summarise, Total = length(MEMO_CONSUMER)) %>%
                      arrange(-Total)

InternalSRM_Action2 <- InternalSRM_Action2 %>%
                      mutate(ACTION = ActionType(FULL_NAME = FULL_NAME.x, ENQUIRY = ENQUIRY, ACTION = ACTION))

InternalSRM_Action_filter2 <- aggregate(Total ~ ACTION, InternalSRM_Action2, sum)

InternalSRM_Action_filter2 <- InternalSRM_Action_filter2 %>%
                   arrange(-Total) %>%  
                   # group_by(ENQUIRY) %>%
                   # summarise(Total = sum(Total)) %>%
                   # ungroup %>%
                   mutate(CumulativePercent = cumsum(Total)/sum(Total)) %>%
                   filter(CumulativePercent < 0.99) %>%
                   dplyr::select(ACTION, Total, CumulativePercent)

InternalSRM_Action2[!(InternalSRM_Action2$ACTION %in% InternalSRM_Action_filter2$ACTION), ]$ACTION <- "OTHER"

InternalSRM_Action2$EXCEPTIONS <- NA
InternalSRM_Action2[grepl("EXCEPTIONS-.*", InternalSRM_Action2$ACTION), ]$EXCEPTIONS <- "TRUE"
InternalSRM_Action2[!grepl("EXCEPTIONS-.*", InternalSRM_Action2$ACTION), ]$EXCEPTIONS <- "FALSE"

InternalSRM_Action2 <- aggregate(Total ~ FY + QUARTER + MONTH + ACC_TYPE + ACTION + EXCEPTIONS, InternalSRM_Action2, sum)

InternalSRM_Action2 <- InternalSRM_Action2 %>%
                      arrange(-Total)

InternalSRM_Action2 <- InternalSRM_Action2 %>%
                       gather(XAXIS, VALUE, ACC_TYPE, QUARTER:MONTH, EXCEPTIONS)


```

Rountine billing exceptions made up `r round(sum(InternalSRM_Action2[grepl("EXCEPTIONS-.*", InternalSRM_Action2$ACTION), ]$Total)/sum(InternalSRM_Action2$Total) * 100, 2)` percent of all non-residential 'internal SRMs' in the 15/16 financial year

The reason for this is currently unknown (please see recommendations)

```{r, include=FALSE, eval = TRUE}

# x <- c("imageUploaded,people.jpg,more,comma,separated,stuff", "imageUploaded", "people.jpg")
# grepl("(?=.*imageUploaded)(?=.*people\\.jpg)", x, perl = TRUE)

Total <- CallQual3 %>% 
  filter(ENQUIRY == "INTERNAL SRM", ACTION == "RECHEK READ") %>%
  group_by(FY, USES) %>%
  dplyr::summarise(n())

Success <- CallQual3 %>% 
  filter(ENQUIRY == "INTERNAL SRM", ACTION == "RECHEK READ") %>%
  mutate(READ_TYPE = ifelse(grepl(".*HIGH READ.*", REPLACE.SR_REMARKS.CHR.63485USINGNCHAR_CS.....), "HIGH", "LOW")) %>%
  #mutate(CONFIRMED = grepl(".*CONFIRMED.*", REPLACE.SR_REMARKS.CHR.63485USINGNCHAR_CS.....)) %>%
  mutate(CONFIRMED_INCORRECT = grepl("(?=.*CONFIRMED)(?=.*INCORRECT)", REPLACE.SR_REMARKS.CHR.63485USINGNCHAR_CS....., perl = TRUE)) %>%
  group_by(USES, READ_TYPE, FY) %>%
  dplyr::summarise(Index = sum(CONFIRMED_INCORRECT=="TRUE")/ sum(CONFIRMED_INCORRECT=="FALSE")) %>%
  ungroup() %>%
  spread(READ_TYPE, Index)

test <- CallQual3 %>% 
  filter(ENQUIRY == "INTERNAL SRM", ACTION == "RECHEK READ") %>%
  mutate(READ_TYPE = ifelse(grepl(".*HIGH READ.*", REPLACE.SR_REMARKS.CHR.63485USINGNCHAR_CS.....), "HIGH", "LOW")) %>%
  #mutate(CONFIRMED = grepl(".*CONFIRMED.*", REPLACE.SR_REMARKS.CHR.63485USINGNCHAR_CS.....)) %>%
  mutate(CONFIRMED_INCORRECT = grepl("(?=.*CONFIRMED)(?=.*INCORRECT)", REPLACE.SR_REMARKS.CHR.63485USINGNCHAR_CS....., perl = TRUE)) %>%
  group_by(CONFIRMED_INCORRECT, USES, READ_TYPE, FY) %>%
  dplyr::summarise(Total = n())%>%
  ungroup() %>%
  spread(READ_TYPE, Total) 

identical(Success[Success$USES == "NONRES" & Success$FY == 2015,]$HIGH, 
          test[test$USES == "NONRES" & test$FY == 2015 & test$CONFIRMED_INCORRECT == TRUE,]$HIGH/test[test$USES == "NONRES" & test$FY == 2015 & test$CONFIRMED_INCORRECT == FALSE,]$HIGH)



  

```

```{r Events, include=FALSE, eval = FALSE}

sample <- CallQual3 %>%
          filter(substring(MEMO_CONSUMER, 1, 2) != "99") %>%
          group_by(FY, yday(MEMO_DATETIME), MEMO_CONSUMER) %>%
          dplyr::summarise(Total = n()) %>%
          arrange(-Total) %>%
          head(1)

Events <- CallQual3 %>%
          select(MEMO_CONSUMER, MEMO_ID, MEMO_DATETIME) %>%
          #filter(MEMO_CONSUMER == 12222979611, year(MEMO_DATETIME) == 2015) %>%
          arrange(MEMO_CONSUMER, MEMO_DATETIME) %>%
          mutate(timediff = (MEMO_DATETIME - lag(MEMO_DATETIME, 1))/60,
                 test = timediff < 10)


sourceCpp("C:/Users/farrelp1/Documents/Enquiries/R/Event.cpp")

Events$id <- Event(Events$MEMO_CONSUMER, as.numeric(Events$timediff))

# Events$id <- NA
# Events$id[1] <- 1
# 
# id <- 1
# 
# for(i in seq_along(Events$MEMO_CONSUMER)[-1]) {
#   
#   if(Events$test[i] == FALSE | Events$MEMO_CONSUMER[i] != Events$MEMO_CONSUMER[i - 1]) {
#     
#     id <- id + 1
#     Events$id[[i]] <- id
#     print(i)
#     
#   }
#  
#   # else if(Events$MEMO_CONSUMER[i] == Events$MEMO_CONSUMER[i - 1] & Events$test[i] == TRUE){
#   #   
#   #   Events$id[[i]] <- id
#   #   
#   # } 
#   
#   else {
#     
#     Events$id[[i]] <- id
#     print(i)
#     
#   }
#  
# }

#write.csv(Events, "N:/ABR/Output_2_RootCauseSRMandRepeats/Events.csv")



```

```{r, include=FALSE, eval = TRUE}

Recheck <- CallQual3 %>% 
  filter(ENQUIRY == "INTERNAL SRM", ACTION == "RECHEK READ") %>%
  mutate(READ_TYPE = ifelse(grepl(".*HIGH READ.*", REPLACE.SR_REMARKS.CHR.63485USINGNCHAR_CS.....), "HIGH", "LOW")) %>%
  #mutate(CONFIRMED = grepl(".*CONFIRMED.*", REPLACE.SR_REMARKS.CHR.63485USINGNCHAR_CS.....)) %>%
  mutate(CONFIRMED_INCORRECT = grepl("(?=.*CONFIRMED)(?=.*INCORRECT)", REPLACE.SR_REMARKS.CHR.63485USINGNCHAR_CS....., perl = TRUE)) 

Estimates <- CallQual3 %>%
             filter(ENQUIRY == "METERING")

Cross <- select(Recheck, MEMO_CONSUMER , MEMO_DATETIME, MEMO_ID, FULL_NAME.x, READ_TYPE, CONFIRMED_INCORRECT) %>%
         left_join(select(Estimates, MEMO_CONSUMER , MEMO_DATETIME, MEMO_ID, FULL_NAME.x, ACTION), by = "MEMO_CONSUMER")
         

```

```{r, include=FALSE, eval = FALSE}

process <- CallQual3 %>%
           select(MEMO_CONSUMER, MEMO_DATETIME, ENQUIRY, ACTION, RESULT)

sample <- process %>%
          sample_n(10000)

obj.L<-dataLoader(); # create a Loader
# Load a .csv using "DES" and "ID" as column names to indicate events
# and Patient's ID
obj.L$load.data.frame(sample,
IDName = "MEMO_CONSUMER",EVENTName = "ENQUIRY", dateColumnName = "MEMO_DATETIME")
# now create an object cluster_expectationMaximization
obj.clEM<- cluster_expectationMaximization();
# load the data into logInspector object
obj.clEM$loadDataset( obj.L$getData() );
# perform clustering computation
obj.clEM$calculateClusters(num = 5, typeOfModel = "firstOrderMarkovModel");
# get calculated clusters
a <- obj.clEM$getClusters();
# get informations about performance of clusters
b <- obj.clEM$getClusterStats();
# get log of each iteration of the algorithm
d <- obj.clEM$getClusterLog();

dataList <- obj.L$getData()
obj.FOMM <- firstOrderMarkovModel()
obj.FOMM$loadDataset(dataList = dataList)

obj.FOMM$trainModel()

obj.FOMM$plot()

print(round(obj.L$getData()$MMatrix.perc, digits = 2))

```

```{r, include=FALSE, eval = FALSE}

data("csv_example", package = "edeaR")

head(csv_example)

csv_example$ACTIVITY_INSTANCE <- 1:nrow(csv_example)

csv_example <- gather(csv_example, LIFECYCLE, TIMESTAMP, -CASE, -ACTIVITY, -ACTIVITY_INSTANCE)
head(csv_example)

```

```{r SRMs, include=FALSE, eval = FALSE}

Events <- read.csv("N:/ABR/Output_2_RootCauseSRMandRepeats/Events.csv", stringsAsFactors = FALSE)

SRM_STEP1 <- CallQual3 %>%
       select(MEMO_CONSUMER, ENQUIRY, MEMO_ID, MEMO_DATETIME, SRM_ID, SR_DATETIME, SOTDESCRIPTION, STAT_DATE) %>%
       #filter(!is.na(SRM_ID)) %>%
       left_join(select(Events, MEMO_CONSUMER, MEMO_ID, id), by = c("MEMO_CONSUMER","MEMO_ID")) %>%
       select(id, ENQUIRY, MEMO_DATETIME, SR_DATETIME) #%>%
       # mutate(START = ymd(gsub("([0-9]*-[0-9]*-[0-9]*)(.*)","\\1",as.character(MEMO_DATETIME)))) %>%
       # mutate(COMPLETE = ifelse(!is.na(SR_DATETIME), 
       #                          ymd(gsub("([0-9]*-[0-9]*-[0-9]*)(.*)","\\1",as.character(SR_DATETIME))),
       #                          ymd(START))) %>%
       # mutate(COMPLETE = date(COMPLETE))
       

SRM_STEP1$START <- as.Date(strptime(SRM_STEP1$MEMO_DATETIME, "%Y-%m-%d") )
#SRM_STEP1$COMPLETE <- ifelse(!is.na()strptime(SRM_STEP1$SR_DATETIME, "%Y-%m-%d")
SRM_STEP1$SR_DATETIME[is.na(SRM_STEP1$SR_DATETIME)] <- as.Date(SRM_STEP1$MEMO_DATETIME[is.na(SRM_STEP1$SR_DATETIME)])
#SRM_STEP1$SR_DATETIME[!is.na(SRM_STEP1$SR_DATETIME)] <- strptime(SRM_STEP1$SR_DATETIME[!is.na(SRM_STEP1$SR_DATETIME)], "%Y-%m-%d")
SRM_STEP1$COMPLETE <-as.Date(strptime(SRM_STEP1$SR_DATETIME, "%Y-%m-%d"))


SRM_STEP1 <- SRM_STEP1 %>%
             select(-MEMO_DATETIME, -SR_DATETIME) %>%
              unique()
                             
SRM_STEP1$ACTIVITY_INSTANCE <- 1:nrow(SRM_STEP1)
  
#length(SRM_STEP1[is.na(SRM$id),])


colnames(SRM_STEP1) <- c("CASE","ACTIVITY", "START", "COMPLETE", "ACTIVITY_INSTANCE")

SRM_STEP2 <- CallQual3 %>%
             select(MEMO_CONSUMER, MEMO_ID, SR_DATETIME, SOTDESCRIPTION, STAT_DATE, SRM_ID) %>%
             filter(!is.na(SRM_ID)) %>%
             left_join(select(Events, MEMO_CONSUMER, MEMO_ID, id), by = c("MEMO_CONSUMER","MEMO_ID")) %>%
             select(id, SOTDESCRIPTION, SR_DATETIME, STAT_DATE)  

SRM_STEP2$START <- as.Date(strptime(SRM_STEP2$SR_DATETIME, "%Y-%m-%d")) 
SRM_STEP2$COMPLETE <- as.Date(SRM_STEP2$START)

SRM_STEP2 <- SRM_STEP2 %>%
             select(-SR_DATETIME, -STAT_DATE) %>%
              unique()

SRM_STEP2$ACTIVITY_INSTANCE <- 1:nrow(SRM_STEP2)

colnames(SRM_STEP2) <- c("CASE","ACTIVITY", "START", "COMPLETE", "ACTIVITY_INSTANCE")

Events_all <- rbind(SRM_STEP1, SRM_STEP2) %>%
              filter(!is.na(CASE)) #%>%
              #gather(LIFECYCLE, TIMESTAMP, -CASE, -ACTIVITY, -ACTIVITY_INSTANCE)


```

```{r To XES, include=FALSE, eval = FALSE}

Events_all$LIFECYCLE <- factor(Events_all$LIFECYCLE, labels = c("start","complete"))

log <- eventlog(eventlog = Events_all, 
                case_id = "CASE",
                activity_id = "ACTIVITY", 
                activity_instance_id = "ACTIVITY_INSTANCE", 
                lifecycle_id = "LIFECYCLE", 
                timestamp = "TIMESTAMP")

#file <- write_xes(log, case_attributes = NULL, file = "N:/ABR/Output_2_RootCauseSRMandRepeats/")

write.csv(Events_all, file = "N:/ABR/Output_2_RootCauseSRMandRepeats/EventsAll.csv")

```

#Recommendations
scope a process review that will answer:

1. why there are so many rountine billing exceptions leading to a recheck read request. Is it due to a conservative approach? or legitamate concerns?

1. Do the recheck read's result in a change to the meter reading or does it remain the same (i.e. what is the 'success' rate of recheck read's) IF the volume of recheck reads are due to a conservative approach how can operator's be given more confidence to accept the original meter reads?

1. Settup a process to track progress towards reducing the number of recheck reads. However, we need to be cautious of Goodhart's law :

"When a measure becomes a target, it ceases to be a good measure." This means that we need to keep a focus on a hollistic measurement of SRMs to make sure that a reduction in
recheck reads isn't leading to spill over into a different type of SRM (i.e. moving the problem around instead of solving it)
